---
title: "R Job Scrape"
author: "Mark Perkins"
date: "2025-09-18"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("k12_he_classification.R")
```
# This Markdown file contains all the code to scrape data from Wyoming's k12 and higher education job postings

## Part 1: Wyoming K12 Data

### Loop K12 data from every district on a direct scraping platform
```{r loop with districts on a direct scraping platform, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(stringr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# k12_district_registry.csv is the single source of truth for every K-12
# district scraped from a real structured platform (Applitrack, TedK12,
# SchoolSpring, RedRoverK12) -- District/Platform/Job_Link, plus Org_ID for
# RedRoverK12's numeric org ID (not derivable from its URL slug alone).
# Replaces three separate, independently-maintained link CSVs
# (Frontline_job_links.csv, tedk12_job_links.csv, springer_job_links.csv)
# that used to carry the SAME district under three different spellings in
# practice ("Converse County School Distrcit 2", "Albany Count School
# District 1", "Campbell County Scholl District 1") -- exactly the
# canonicalize_k12_district() misspellings this project has had to patch
# around downstream for months. One row per district here means one
# spelling to get right, checked by tests/testthat/test-drift-check.R's
# equivalent (registry-consistency is exercised via the pipeline's own
# equivalence tests, not a dedicated schema test since this project's
# existing convention is to test behavior, not file shape). A district
# migrating platforms in the future (several already have -- Butte-style
# moves aren't unique to Montana) is a one-row edit here, not a code change.
#
# fetch_applitrack_postings()/fetch_tedk12_postings()/
# fetch_schoolspring_postings()/fetch_redrover_postings() (all
# direct_api_scrapers.R) are unchanged from their original per-platform
# loops -- only the dispatch is unified. Each district is still logged
# individually via safe_scrape() so one district's outage (a few
# Applitrack tenants genuinely return HTTP 500 from Applitrack's own
# servers, independent of this scraper -- confirmed 2026-08-02) doesn't
# block the rest of the registry.
registry <- read.csv("k12_district_registry.csv", stringsAsFactors = FALSE)

all_direct_data <- list()

for (i in seq_len(nrow(registry))) {
  row <- registry[i, ]

  district_jobs <- switch(row$Platform,
    Applitrack = {
      # tenant_path is everything between applitrack.com/ and /onlineapp/
      # in the district's own URL.
      tenant_path <- sub(".*applitrack\\.com/([^/]+)/onlineapp.*", "\\1", row$Job_Link, ignore.case = TRUE)
      df <- safe_scrape(
        row$District,
        scrape_fn = function() fetch_applitrack_postings(tenant_path),
        expected_cols = c("title", "position", "position2", "date_posted", "location", "closing_date")
      )
      # A district with genuinely zero current openings is indistinguishable
      # from any other empty scrape without a placeholder row -- preserved
      # from the original Applitrack loop's own behavior.
      if (nrow(df) == 0) {
        df <- data.frame(title = "No jobs", position = NA, position2 = NA, date_posted = NA,
                          location = NA, closing_date = NA, stringsAsFactors = FALSE)
      }
      data.frame(title = df$title, date_posted = df$date_posted, position = df$position,
                 location = df$location, url = row$Job_Link, District = row$District,
                 stringsAsFactors = FALSE)
    },
    TedK12 = {
      df <- safe_scrape(
        row$District,
        scrape_fn = function() fetch_tedk12_postings(row$Job_Link),
        expected_cols = c("title", "date_posted", "position", "location", "url")
      )
      if (nrow(df) > 0) {
        data.frame(title = df$title, date_posted = df$date_posted, position = df$position,
                   location = df$location, url = df$url, District = row$District,
                   stringsAsFactors = FALSE)
      } else {
        NULL
      }
    },
    SchoolSpring = {
      domain_name <- sub("^https?://", "", row$Job_Link)
      domain_name <- sub("/$", "", domain_name)
      df <- safe_scrape(
        row$District,
        scrape_fn = function() fetch_schoolspring_postings(domain_name),
        expected_cols = c("Title", "Location", "Posted_Date", "Posting_ID", "Link")
      )
      if (nrow(df) > 0) {
        df$District <- row$District
        normalize_id_backed_k12_postings(df)
      } else {
        NULL
      }
    },
    RedRoverK12 = {
      org_slug <- sub(".*/org/([^/?]+).*", "\\1", row$Job_Link, ignore.case = TRUE)
      df <- safe_scrape(
        row$District,
        scrape_fn = function() fetch_redrover_postings(as.character(row$Org_ID), org_slug),
        expected_cols = c("Title", "Location", "Posted_Date", "Posting_ID", "Link")
      )
      if (nrow(df) > 0) {
        df$District <- row$District
        normalize_id_backed_k12_postings(df)
      } else {
        NULL
      }
    },
    stop("Unknown Platform in k12_district_registry.csv: ", row$Platform)
  )

  if (!is.null(district_jobs) && nrow(district_jobs) > 0) {
    all_direct_data[[length(all_direct_data) + 1]] <- district_jobs
  }
}

direct_all <- bind_rows(all_direct_data)

# Save the extracted data to a CSV file
write.csv(direct_all, "all_direct_k12_job_listings.csv", row.names = FALSE)

```

### Combine all the k12 data include a few manual pulls from unique district sites
#### Be sure to update your manually scraped data
#### This will populate your app folder for your Shiny application
```{r combine all the data into one dataframe, echo=TRUE, warning=FALSE, message=FALSE}
library(stringr)
library(tidyverse)
library(dplyr)
library(lubridate)


standardize_date <- function(x) {

  # Convert factor to character safely
  x <- as.character(x)

  # Remove timezone text like "(UTC)"
  x <- str_remove(x, "\\s*\\(.*\\)$")

  # Parse known formats
  parsed <- parse_date_time(
    x,
    orders = c(
      "b d Y h:M p",   # Oct 23 2025 6:00 AM
      "B d Y h:M p",   # October 23 2025 6:00 AM
      "ymd",
      "mdy",
      "dmy",
      "Y-m-d H:M:S"
    ),
    tz = "UTC",
    quiet = TRUE
  )

  as.Date(parsed)
}



direct <- read.csv("all_direct_k12_job_listings.csv", stringsAsFactors = FALSE)

# The 12 districts not on any major platform were previously hand-
# maintained in otherjobs.xlsx (no code in this repo ever wrote that
# file -- it was 5 months stale). Replaced with a real pipeline: WSBA's
# statewide vacancies page (clean structured data, but confirmed
# incomplete -- misses ~60-75% of real postings, systematically dropping
# classified/support/substitute/coaching roles) combined with each
# district's own page (heuristic per-platform extraction, deduplicated
# against that district's WSBA entries by normalized title). See
# misc_district_scrapers.R's header comment for the full platform
# breakdown and known limitations.
source("scrape_helpers.R")
source("direct_api_scrapers.R")
source("misc_district_scrapers.R")

other <- safe_scrape(
  "Miscellaneous K-12 districts (WSBA + own pages)",
  scrape_fn = function() {
    fetch_all_misc_district_postings(
      chromote_session_factory = function() chromote::ChromoteSession$new()
    )
  },
  expected_cols = c("title", "date_posted", "position", "location", "url", "District")
)

# Laramie Montessori Charter School: not a school district at all (so it
# has no natural home in misc_district_registry, which is keyed by
# District), but was found to have its own clean structured source
# (Paylocity) while investigating Wyoming's charter schools -- see
# direct_api_scrapers.R::fetch_paylocity_jobs(). Snowy Range Academy, the
# other real charter school found, already surfaces via WSBA with no
# extra code needed since WSBA already treats it as a standalone org.
laramie_montessori <- safe_scrape(
  "Laramie Montessori Charter School",
  scrape_fn = function() fetch_paylocity_jobs("70f7d03b-6c9f-4106-8e70-9d781a8bbcba", "Laramie-Montessori-School-Inc"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)
if (nrow(laramie_montessori) > 0) {
  laramie_montessori <- data.frame(
    title = laramie_montessori$Title,
    date_posted = laramie_montessori$Posted_Date,
    position = NA_character_,
    location = laramie_montessori$Location,
    url = laramie_montessori$Link,
    District = "Laramie Montessori Charter School",
    stringsAsFactors = FALSE
  )
  other <- dplyr::bind_rows(other, laramie_montessori)
}

direct <- direct %>%
  mutate(date_posted = standardize_date(date_posted))

other <- other %>%
  mutate(date_posted = standardize_date(date_posted))

is_wsba <- !is.na(other$url) & other$url == WSBA_VACANCIES_URL
wsba_rows <- remove_wsba_direct_duplicates(other[is_wsba, , drop = FALSE], direct)
other_rows <- other[!is_wsba, , drop = FALSE]

combined <- dplyr::bind_rows(direct, other_rows, wsba_rows) %>%
  mutate(Archive_Date = Sys.Date())

# fix_title_encoding() (k12_he_classification.R) is applied here, once, at
# the point titles first enter the pipeline -- not just inside
# classify_k12_position()/classify_k12_subject() below, which only fixed a
# private copy used for regex matching and discarded it. Without this, a
# title with a raw Windows-1252 byte (an en dash in a time range, etc.) from
# any non-Applitrack source (TedK12/SchoolSpring/RedRover/misc-district) would
# classify correctly but still archive and display with the mangled byte,
# since the archived CSV below and combinedclean's `title` column both come
# from this same `combined` object.
combined <- combined %>%
  mutate(
    title = fix_title_encoding(title),
    posting_id = build_k12_posting_id(
      source_id = posting_id,
      title = title,
      location = location,
      date_posted = date_posted,
      url = url,
      district = canonicalize_k12_district(District)
    )
  )

file_name <- paste0("combined_", Sys.Date(), ".csv")

# Write the data to a CSV file with the new file name
write.csv(combined, file=file.path('Archivek12_Data',file_name), row.names = FALSE)

# Categorize positions in the "position" column of the "combinedclean" dataset.
# classify_k12_position() lives in k12_he_classification.R (sourced above) so
# this week's raw jobs-table classification and the accumulated-history
# append below can't silently drift apart.

combinedclean <- combined %>%
  mutate(position = classify_k12_position(title),
         District = canonicalize_k12_district(District)) %>%
  dplyr::select(title, Archive_Date, date_posted, position, location, url, posting_id, District)

write.csv(combinedclean, file=file.path('Wy_Ed_Jobs','combinedclean.csv'), row.names = FALSE)

#--------------------------------------------------------------------------
# Append this week's newly classified rows onto the existing accumulated
# history, instead of reprocessing every archived raw snapshot from
# scratch every run -- see history_accumulator.R's header for why (100+
# archive files and growing, O(all history) work every week on a 30-minute
# CI budget). append_weekly_rows() is idempotent (a same-day re-run
# replaces, not duplicates, that day's rows) and asserts the new week's
# columns match the existing file's before writing anything.
#
# For disaster recovery, or to independently verify this incremental path
# hasn't drifted, scripts/rebuild_k12_history_from_archive.R rebuilds these
# same files from scratch from the raw archive -- that's also what
# tests/testthat/test-history-accumulator.R checks this incremental path
# against, using the real archived data in this repo.
#--------------------------------------------------------------------------
source("history_accumulator.R")

this_week_k12jobs <- combinedclean %>%
  filter(position == "Teacher") %>%
  mutate(Category = classify_k12_subject(title),
         Broad_Category = classify_k12_broad_category(Category)) %>%
  dplyr::select(title, Archive_Date, position, location, url, posting_id, District, Category, Broad_Category)

k12jobs <- append_weekly_rows(file.path("Wy_Ed_Jobs", "k12jobanalysis.csv"), this_week_k12jobs)
write.csv(k12jobs, file=file.path('Wy_Ed_Jobs','k12jobanalysis.csv'), row.names = FALSE)

# Per-district weekly posting totals (ALL categories, not just Teacher) --
# powers the sparkline trend shown next to each district's raw count on
# the landing page's "Top K-12 Hiring Districts" table. Built from the
# same combinedclean used above, just not filtered to position == "Teacher".
this_week_district_totals <- combinedclean %>%
  count(District, Archive_Date, name = "n")
k12_district_weekly_totals <- append_weekly_rows(
  file.path("Wy_Ed_Jobs", "k12_district_weekly_totals.csv"), this_week_district_totals)
write.csv(k12_district_weekly_totals, file.path("Wy_Ed_Jobs", "k12_district_weekly_totals.csv"), row.names = FALSE)


#Database for all dates by category
# Dedup key is posting_id, not title+location: two real vacancies can have
# identical display text but distinct source IDs (as SchoolSpring does).
#
# The Total row is computed as the SUM of the per-district counts below, not
# as its own independent n_distinct() over every district's rows combined.
# Some scrapers fall back to a generic location placeholder (literally the
# string "District") when they can't extract a real school name, and two
# different districts can both produce that same generic title+location
# combination for two genuinely different real postings; deduping across
# district boundaries would silently collapse those into one and undercount
# the Total relative to its own parts.
#
# Both this week's Total and per-district rows are computed from
# this_week_k12jobs alone (one Archive_Date), not the full accumulated
# k12jobs -- the group_by already includes Archive_Date, so each week's
# counts are independent of every other week's, and only this week's
# slice needs to be computed fresh.
this_week_k12sumdistrict <- summarize_k12_posting_counts(this_week_k12jobs)

this_week_k12sum <- this_week_k12sumdistrict %>%
  group_by(Broad_Category, Archive_Date) %>%
  summarize(sum = sum(sum), .groups = "drop") %>%
  mutate(District = "Total") %>%
  select(Broad_Category, Archive_Date, District, sum)

# Consistency check for the append logic itself, not the underlying data --
# this week's Total must equal the sum of this week's own district rows
# before either is ever written to the accumulated history. See
# history_accumulator.R::check_total_matches_parts().
check_total_matches_parts(this_week_k12sum, this_week_k12sumdistrict,
                           group_cols = c("Broad_Category", "Archive_Date"))

this_week_allsum <- bind_rows(this_week_k12sum, this_week_k12sumdistrict)
Allsum <- append_weekly_rows(file.path("Wy_Ed_Jobs", "allsum.csv"), this_week_allsum)
write.csv(Allsum, file=file.path('Wy_Ed_Jobs','allsum.csv'), row.names = FALSE)

# Database for all data NOW by category -- always just this week's
# snapshot, so unlike the datasets above this never needed the archive
# rebuild in the first place; it's built straight from this week's own
# district-level summary computed above.
k12districtnowsum <- this_week_k12sumdistrict %>%
  ungroup() %>%
  rename(Sum = sum) %>%
  select(Broad_Category, Sum, District)

k12nowsum <- k12districtnowsum %>%
  group_by(Broad_Category) %>%
  summarize(Sum = sum(Sum), .groups = "drop") %>%
  mutate(District = "Total")

Allnow <- bind_rows(k12nowsum, k12districtnowsum)

write.csv(Allnow, file=file.path('Wy_Ed_Jobs','allnow.csv'), row.names = FALSE)

list<-unique(this_week_k12jobs$District)
write.csv(list, "list.csv", row.names = FALSE)
```

### K-12 salary data, from WSBA's publicly shared PDFs
```{r wsba salary data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("salary_scrapers.R")

teacher_salary <- safe_scrape(
  "WSBA teacher salary settlements",
  scrape_fn = fetch_wsba_teacher_salary,
  expected_cols = c("District", "Base_Salary_Prior_Year", "Base_Salary_Current_Year", "Salary_Year")
)

superintendent_salary <- safe_scrape(
  "WSBA superintendent salaries",
  scrape_fn = fetch_wsba_superintendent_salary,
  expected_cols = c("District", "Superintendent_Salary", "Superintendent_Contract_Days")
)

# Static geo/link fields (County, Latitude, Longitude, Link, Job_Link)
# stay hand-maintained -- only the salary figures get refreshed from WSBA
# each run. District is already canonical in the file on disk.
salarymap2 <- read.csv(file.path("Wy_Ed_Jobs", "salarymap2.csv"), fileEncoding = "UTF-8") %>%
  select(District, County, Latitude, Longitude, Link, Job_Link)

if (nrow(teacher_salary) > 0 && nrow(superintendent_salary) > 0) {
  salarymap2 <- salarymap2 %>%
    left_join(teacher_salary, by = "District") %>%
    left_join(superintendent_salary, by = "District") %>%
    rename(Teacher_Base_Salary = Base_Salary_Current_Year,
           Teacher_Base_Salary_Prior_Year = Base_Salary_Prior_Year) %>%
    # No "last updated" timestamp -- this data only changes once a year
    # (WSBA republishes a new Salary_Year settlement document), so a date
    # stamped fresh on every weekly pipeline run would just mislead people
    # into thinking the dollar figures themselves refresh that often.
    # Salary_Year is the real freshness signal.
    mutate(Salary_Source = "WSBA (wsba-wy.org)") %>%
    select(District, County, Latitude, Longitude, Link, Job_Link,
           Teacher_Base_Salary, Teacher_Base_Salary_Prior_Year, Salary_Year,
           Superintendent_Salary, Superintendent_Contract_Days,
           Salary_Source)

  write.csv(salarymap2, file.path("Wy_Ed_Jobs", "salarymap2.csv"), row.names = FALSE)

  # Starts building a multi-year K-12 salary trend -- WSBA has no public
  # historical archive (unlike IPEDS, checked directly 2026-08-05), so
  # this only accumulates real history going forward, one snapshot per
  # new Salary_Year.
  archive_k12_salary_snapshot(salarymap2, file.path("Wy_Ed_Jobs", "k12_salary_history.csv"))
} else {
  message("WSBA salary fetch failed for one or both documents -- leaving salarymap2.csv untouched this run.")
}

# District-level data-completeness classification (misc_district_scrapers.R)
# -- refreshed unconditionally every run, not gated on the salary fetch
# above, since it's a static structural fact about which platform each
# district is scraped from, not something that can itself fail to fetch.
# Every district not in misc_district_coverage_tiers() is scraped from a
# genuine structured job-board platform, hence the coalesce to "Full".
source("misc_district_scrapers.R")
salarymap2 <- read.csv(file.path("Wy_Ed_Jobs", "salarymap2.csv"), fileEncoding = "UTF-8") %>%
  select(-any_of("Data_Coverage")) %>%
  left_join(misc_district_coverage_tiers(), by = "District") %>%
  mutate(Data_Coverage = coalesce(Data_Coverage, "Full"))
write.csv(salarymap2, file.path("Wy_Ed_Jobs", "salarymap2.csv"), row.names = FALSE)
```

### K-12 teacher FTE (staff headcount), from NCES's Common Core of Data via the Urban Institute API
```{r ccd teacher fte data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("ccd_staff_scraper.R")

teacher_fte <- safe_scrape(
  "CCD district teacher FTE (WY)",
  scrape_fn = fetch_ccd_teacher_fte,
  expected_cols = c("District", "Teachers_Total_FTE", "Enrollment", "CCD_Year")
)

salarymap2 <- read.csv(file.path("Wy_Ed_Jobs", "salarymap2.csv"), fileEncoding = "UTF-8")

if (nrow(teacher_fte) > 0) {
  # No "last updated" timestamp -- same reasoning as the WSBA/IPEDS salary
  # chunks. CCD_Year is the real freshness signal for this data.
  salarymap2 <- salarymap2 %>%
    left_join(teacher_fte, by = "District") %>%
    mutate(CCD_Source = "NCES Common Core of Data via Urban Institute Education Data Portal (educationdata.urban.org)")

  write.csv(salarymap2, file.path("Wy_Ed_Jobs", "salarymap2.csv"), row.names = FALSE)
} else {
  message("CCD teacher FTE fetch failed -- leaving salarymap2.csv untouched this run.")
}
```

### County-level context (income, rent, mining/energy employment share, population trend), from the Census Bureau's ACS 5-Year Estimates
```{r census county context data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("census_acs_scraper.R")

# CENSUS_API_KEY must be set (a GitHub Actions secret in CI, .Renviron
# locally) -- see census_acs_scraper.R's header for why this can't run
# without one. safe_scrape() catches a missing/invalid key the same way it
# catches any other fetch failure: logs it, leaves salarymap2.csv
# untouched this run, rather than crashing the whole pipeline.
county_context <- safe_scrape(
  "Census ACS county context (WY)",
  scrape_fn = fetch_census_county_context,
  expected_cols = c("County", "Median_Household_Income", "Median_Gross_Rent",
                     "Population", "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct")
)

if (nrow(county_context) > 0) {
  # Joins on County, not District -- one County value maps to multiple
  # sibling districts (e.g. Sheridan County SD1 and SD2 both correctly
  # get the same Sheridan County figures), same one-to-many relationship
  # WSBA's own District-level salary data doesn't have but this genuinely
  # does. No "last updated" timestamp, same reasoning as the WSBA/CCD/
  # IPEDS chunks above -- ACS_Year is the real freshness signal, and this
  # is 5-year-smoothed data that doesn't meaningfully change week to week.
  # select(-any_of(...)) drops last run's copy of these columns first so
  # a re-run doesn't produce Median_Household_Income.x/.y duplicates --
  # only reached on a successful fetch, so a failed run leaves the
  # existing columns (and every other column) fully untouched, same as
  # every other salary/staffing chunk in this pipeline.
  salarymap2 <- read.csv(file.path("Wy_Ed_Jobs", "salarymap2.csv"), fileEncoding = "UTF-8") %>%
    select(-any_of(c("Median_Household_Income", "Median_Gross_Rent", "Population",
                      "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct"))) %>%
    left_join(county_context, by = "County")
  write.csv(salarymap2, file.path("Wy_Ed_Jobs", "salarymap2.csv"), row.names = FALSE)
} else {
  message("Census ACS county context fetch failed -- leaving salarymap2.csv untouched this run.")
}
```

### District-level child poverty rate, from the Census Bureau's SAIPE program
```{r census saipe child poverty data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("census_acs_scraper.R")  # census_saipe_scraper.R reuses census_api_key()/clean_acs_value()/WY_STATE_FIPS from here
source("census_saipe_scraper.R")

child_poverty <- safe_scrape(
  "Census SAIPE district child poverty rate (WY)",
  scrape_fn = fetch_census_saipe_child_poverty,
  expected_cols = c("District", "Child_Poverty_Rate", "SAIPE_Year")
)

if (nrow(child_poverty) > 0) {
  # Joins on District, not County -- real district-level data (the closest
  # free proxy to free/reduced-lunch eligibility at the actual district a
  # posting is in), unlike the county-context chunk above. Fremont County
  # School District 38 (Arapahoe Charter High School) is a confirmed real
  # gap in SAIPE's own coverage -- left as a genuine NA after this join,
  # not something to force-match.
  salarymap2 <- read.csv(file.path("Wy_Ed_Jobs", "salarymap2.csv"), fileEncoding = "UTF-8") %>%
    select(-any_of(c("Child_Poverty_Rate", "SAIPE_Year"))) %>%
    left_join(child_poverty, by = "District")
  write.csv(salarymap2, file.path("Wy_Ed_Jobs", "salarymap2.csv"), row.names = FALSE)
} else {
  message("Census SAIPE child poverty fetch failed -- leaving salarymap2.csv untouched this run.")
}
```


## Time to scrape Wyoming Higher Education Data
### This chunk scrapes LCCC's data
```{r Get Jobs from LCCC, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# LCCC is on the same NEOGOV platform as Casper/Central/Gillette/Western,
# just under the governmentjobs.com domain instead of schooljobs.com --
# fetch_neogov_postings() takes the domain as a parameter for exactly this
# reason. Replaces the old RSelenium scraper (manual scroll + wait-for-
# element polling) with a single direct HTTP call.
lccc_raw <- safe_scrape(
  "Laramie County Community College",
  scrape_fn = function() fetch_neogov_postings("https://www.governmentjobs.com", "lcccwy"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

lccc <- lccc_raw %>%
  mutate(Institution = "Laramie County Community College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(lccc)

```

### This pulls data from Casper College
```{r casper college, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

casper_raw <- safe_scrape(
  "Casper College",
  scrape_fn = function() fetch_neogov_postings("https://www.schooljobs.com", "caspercollege"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

casper <- casper_raw %>%
  mutate(Institution = "Casper College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(casper)

```


### This pulls jobs data from Western Wyoming
```{r western wyoming, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Western is on the same PeopleAdmin platform as Eastern/Sheridan/
# Northwest, not NEOGOV -- a prior investigation mistyped the domain as
# "wwccwy.peopleadmin.com" (double-c), got NXDOMAIN, and wrongly concluded
# Western had migrated to schooljobs.com/careers/westernwyoming (a real
# NEOGOV agency slug that happens to return a valid "0 jobs found" page,
# not Western's actual career site). The real domain is
# "wwcwy.peopleadmin.com" (single-c) -- confirmed live with 46 real open
# postings, silently missed by the NEOGOV version for an unknown period.
western_raw <- safe_scrape(
  "Western Wyoming Community College",
  scrape_fn = function() fetch_peopleadmin_atom("https://wwcwy.peopleadmin.com/postings/all_jobs", "Western Wyoming Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

western <- western_raw %>%
  mutate(Institution = "Western Wyoming Community College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(western)

```


### This pulls data from Central Wyoming college
```{r central wyoming, message=FALSE, echo=TRUE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

central_raw <- safe_scrape(
  "Central Wyoming College",
  scrape_fn = function() fetch_neogov_postings("https://www.schooljobs.com", "cwc"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

central <- central_raw %>%
  mutate(Institution = "Central Wyoming College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(central)

```

### This pulls jobs data from Eastern Wyoming college
```{r Eastern, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Eastern's own published Atom feed replaces the old RSelenium scraper
# entirely -- see direct_api_scrapers.R::fetch_peopleadmin_atom(). No
# browser, no pagination, no CSS selectors to drift.
eastern_raw <- safe_scrape(
  "Eastern Wyoming Community College",
  scrape_fn = function() fetch_peopleadmin_atom("https://ewc.peopleadmin.com/postings/all_jobs", "Eastern Wyoming Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

eastern <- eastern_raw %>%
  mutate(Institution = "Eastern Wyoming Community College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(eastern)

```

### This pulls data Gillette college
```{r gillette, message=FALSE, echo=TRUE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

gillette_raw <- safe_scrape(
  "Gillette College",
  scrape_fn = function() fetch_neogov_postings("https://www.schooljobs.com", "gillettecollege"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

gillette <- gillette_raw %>%
  mutate(Institution = "Gillette College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(gillette)

```
### This pulls data from Sheridan College
```{r sheridan, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Sheridan is on the same PeopleAdmin platform as Eastern Wyoming --
# confirmed by matching asset hashes/scripts -- so the same Atom feed
# approach applies. Replaces the old RSelenium scraper (which navigated to
# every individual job's detail page just to read its posting date).
sheridan_raw <- safe_scrape(
  "Sheridan College",
  scrape_fn = function() fetch_peopleadmin_atom("https://jobs.sheridan.edu/postings/all_jobs", "Sheridan College Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

sheridan <- sheridan_raw %>%
  mutate(Institution = "Sheridan College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(sheridan)

```

### This pulls data from Northwest College
```{r Northwest, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Northwest is also on the same PeopleAdmin platform, white-labeled under
# the simplehire.com domain -- confirmed by matching asset hashes/scripts
# despite the different-looking hostname and previously different
# selectors. Same Atom feed approach as Eastern/Sheridan.
northwest_raw <- safe_scrape(
  "Northwest College",
  scrape_fn = function() fetch_peopleadmin_atom("https://northwestcollege.simplehire.com/postings/all_jobs", "Northwest College Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

northwest <- northwest_raw %>%
  mutate(Institution = "Northwest College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(northwest)

```



### This pulls data from the University of Wyoming
```{r university of Wyoming}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# UW's Oracle Cloud HCM recruiting platform exposes a public JSON REST API
# (see direct_api_scrapers.R::fetch_uw_postings()) that fully replaces the
# old RSelenium scraper -- no infinite-scroll simulation, no
# findElements()-based text scraping, no waiting on JS to render.
UW_raw <- safe_scrape(
  "University of Wyoming",
  scrape_fn = fetch_uw_postings,
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

UW <- UW_raw %>%
  mutate(Institution = "University of Wyoming") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(UW)

```

### Combine all the Higher Education data
#### This will populate your app folder for your Shiny application
```{r munge he data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(writexl)
library(tidyverse)
library(readxl)

# Combine all datasets
hedata <- rbind(lccc, casper, western, central, eastern, gillette, sheridan, northwest, UW)

hedata$Posted_Date<- as.character(hedata$Posted_Date)

hedata <- hedata %>%
  mutate(Archive_Date = Sys.Date())

# Save data with a time stamp
file_name <- paste0("hedata_", Sys.Date(), ".xlsx")

write_xlsx(hedata, path = file_name)

write_xlsx(hedata, path = file.path("Archived_HE_Data", file_name))
write_xlsx(hedata, path = file.path("Wy_Ed_Jobs", "hedata.xlsx"))

# Fix historical institution-name typos before anything downstream keys off
# Institution, so a college's history doesn't silently split across two
# spellings (see canonicalize_he_institution() in k12_he_classification.R).
# Applied to this week's raw hedata AFTER the xlsx archive writes above, so
# the archived raw snapshot keeps whatever spelling the scraper actually
# produced that week (the historical record of what really happened),
# while everything derived from here on uses the canonical name.
hedata <- hedata %>%
  mutate(Institution = canonicalize_he_institution(Institution))

# Job_Type/Category classification lives in k12_he_classification.R (sourced
# in setup). Adjunct/pooled titles get their own Job_Type, separate from
# "Instructor/Teacher/Faculty", so a standing adjunct-pool posting isn't
# counted the same as full-time faculty hiring.
this_week_he_cat <- hedata %>%
  mutate(Job_Type = classify_he_job_type(Title))

this_week_facultydata <- this_week_he_cat %>%
  filter(Job_Type %in% c("Instructor/Teacher/Faculty", "Adjunct/Part-Time Faculty")) %>%
  mutate(Category = classify_he_faculty_category(Title))

#--------------------------------------------------------------------------
# Append this week's newly classified rows onto the existing accumulated
# history, instead of reprocessing every archived raw xlsx snapshot from
# scratch every run. See history_accumulator.R's header (also sourced in
# the K-12 chunk above -- sourcing again here is a cheap no-op) and
# scripts/rebuild_he_history_from_archive.R for the disaster-recovery /
# verification path.
#--------------------------------------------------------------------------
source("history_accumulator.R")

facultydata <- append_weekly_rows(file.path("Wy_Ed_Jobs", "facultydata.csv"), as.data.frame(this_week_facultydata))
# Also shipped to the repo root (gitignored/local-only) mirroring the
# Wy_Ed_Jobs/ copy, same as before.
write.csv(facultydata, "facultydata.csv", row.names = FALSE)
write.csv(facultydata, file.path("Wy_Ed_Jobs", "facultydata.csv"), row.names = FALSE)

# Per-institution weekly posting totals (ALL categories/job types, not
# just full-time faculty) -- powers the sparkline trend shown next to
# each institution's raw count on the landing page's "Top Higher Ed
# Hiring Institutions" table. Built from this week's hedata (already
# canonicalized above) before the Job_Type/faculty-only filter.
this_week_he_totals <- hedata %>%
  count(Institution, Archive_Date, name = "n")
he_institution_weekly_totals <- append_weekly_rows(
  file.path("Wy_Ed_Jobs", "he_institution_weekly_totals.csv"), this_week_he_totals)
write.csv(he_institution_weekly_totals, file.path("Wy_Ed_Jobs", "he_institution_weekly_totals.csv"), row.names = FALSE)

# facultydata includes both full-time-ish and Adjunct/Part-Time faculty
# (Job_Type column distinguishes them) so the "Current Faculty Trends"
# chart can show a full-time/part-time stacked breakdown; the Longitudinal
# Trends and New This Week views filter back down to Job_Type ==
# "Instructor/Teacher/Faculty" in app.R to keep their existing, unchanged
# meaning ("faculty hiring", not incl. the standing adjunct pool).
#
# Both this week's Total and per-institution rows are computed from
# this_week_facultydata alone (one Archive_Date) -- same reasoning as the
# K-12 allsum block above.
this_week_hesum <- this_week_facultydata %>%
  group_by(Category, Archive_Date, Job_Type) %>%
  summarize(sum = n(), .groups = "drop") %>%
  mutate(Institution = "Total") %>%
  select(Category, Archive_Date, Institution, Job_Type, sum)

this_week_hesuminst <- this_week_facultydata %>%
  group_by(Category, Archive_Date, Institution, Job_Type) %>%
  summarise(sum = n(), .groups = "drop")

check_total_matches_parts(this_week_hesum, this_week_hesuminst,
                           group_cols = c("Category", "Archive_Date", "Job_Type"))

this_week_allsum_he <- bind_rows(this_week_hesum, this_week_hesuminst)
Allsum_he <- append_weekly_rows(file.path("Wy_Ed_Jobs", "allsum_he.csv"), this_week_allsum_he)
write.csv(Allsum_he, file = file.path("Wy_Ed_Jobs", "allsum_he.csv"), row.names = FALSE)

# Database for all data NOW by category -- always just this week's
# snapshot, built straight from this_week_facultydata (no history needed).
henowsum <- this_week_hesum %>%
  ungroup() %>%
  rename(Sum = sum) %>%
  select(Category, Job_Type, Sum, Institution)

henowinstsum <- this_week_facultydata %>%
  group_by(Category, Institution, Job_Type) %>%
  summarize(Sum = n(), .groups = "drop") %>%
  select(Category, Sum, Institution, Job_Type)

Allnow_he <- rbind(henowsum, henowinstsum)

write.csv(Allnow_he, file = file.path("Wy_Ed_Jobs", "allnow_he.csv"), row.names = FALSE)
```

### Higher Ed faculty salary data, from IPEDS via the Urban Institute's Education Data Portal API
```{r ipeds he salary data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("ipeds_salary_scraper.R")

he_salary <- safe_scrape(
  "IPEDS instructional staff salaries (WY)",
  scrape_fn = fetch_ipeds_he_salaries,
  expected_cols = c("Name", "Faculty_Avg_Salary", "Faculty_Avg_Salary_Professor",
                     "Faculty_Count", "Salary_Year", "Salary_Note")
)

# Static geo/link fields (Longitude, Latitude, Link, County) stay hand-
# maintained -- only the salary figures get refreshed from IPEDS each run.
# County (added 2026-08-06) is the join key the census county context
# chunk below needs; kept here in this early select() so it survives
# untouched through this chunk the same way Longitude/Latitude/Link do.
salarymap <- read.csv(file.path("Wy_Ed_Jobs", "salarymap.csv"), fileEncoding = "UTF-8") %>%
  select(Name, Longitude, Latitude, Link, County)

if (nrow(he_salary) > 0) {
  # No "last updated" timestamp -- same reasoning as the WSBA chunk above.
  # IPEDS reports this annually (Salary_Year is the real freshness signal),
  # so stamping today's date every weekly run would misrepresent how often
  # the actual dollar figures change.
  salarymap <- salarymap %>%
    left_join(he_salary, by = "Name") %>%
    mutate(Salary_Source = "IPEDS via Urban Institute Education Data Portal (educationdata.urban.org)")

  # Multi-year salary trend (current + 2 prior years) -- IPEDS is
  # queryable by year indefinitely, unlike WSBA (no public historical
  # archive; checked directly 2026-08-05). Pivoted to generic "N years
  # ago" column names, not literal year numbers, so the schema stays
  # stable as the calendar year rolls over -- app.R derives the real
  # year labels from Salary_Year - 1, Salary_Year - 2.
  salary_trend <- fetch_ipeds_he_salary_trend(n_years = 3)
  if (nrow(salary_trend) > 0) {
    latest_year <- max(salary_trend$Year)
    salary_trend_wide <- salary_trend %>%
      mutate(YearsAgo = latest_year - Year) %>%
      filter(YearsAgo > 0) %>%
      select(Name, YearsAgo, Faculty_Avg_Salary) %>%
      tidyr::pivot_wider(names_from = YearsAgo, values_from = Faculty_Avg_Salary,
                          names_glue = "Faculty_Avg_Salary_Y{YearsAgo}Ago")
    salarymap <- salarymap %>% left_join(salary_trend_wide, by = "Name")
  }

  salarymap <- salarymap %>%
    select(Name, Longitude, Latitude, Link, County, Faculty_Avg_Salary, Faculty_Avg_Salary_Professor,
           Faculty_Count, Salary_Year, Salary_Note, Salary_Source,
           starts_with("Faculty_Avg_Salary_Y"))

  write.csv(salarymap, file.path("Wy_Ed_Jobs", "salarymap.csv"), row.names = FALSE)
} else {
  message("IPEDS salary fetch failed -- leaving salarymap.csv untouched this run.")
}
```

### Higher ed institution fall enrollment (FTE), from IPEDS via the Urban Institute's Education Data Portal API
```{r ipeds he enrollment data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("ipeds_salary_scraper.R")  # ipeds_enrollment_scraper.R reuses fetch_ipeds_paginated()/IPEDS_UNITID_MAP from here
source("ipeds_enrollment_scraper.R")

he_enrollment <- safe_scrape(
  "IPEDS fall enrollment FTE (WY)",
  scrape_fn = fetch_ipeds_he_enrollment,
  expected_cols = c("Name", "Enrollment", "Enrollment_Year")
)

# 5-year enrollment trend -- HE's analogue of the Census county context
# chunk's Population_Change_Pct, just at the institution level. A second,
# independent safe_scrape() call (like teacher_salary/superintendent_
# salary in the WSBA chunk above) rather than folded into
# fetch_ipeds_he_enrollment() itself, so a trend-fetch failure (a missing
# 5-years-back vintage) doesn't also block this week's current Enrollment
# figure from updating.
he_enrollment_trend <- safe_scrape(
  "IPEDS fall enrollment 5-year trend (WY)",
  scrape_fn = fetch_ipeds_he_enrollment_trend,
  expected_cols = c("Name", "Enrollment_Change_Pct")
)

if (nrow(he_enrollment) > 0) {
  # No "last updated" timestamp -- same reasoning as every other salary/
  # staffing chunk. Enrollment_Year is the real freshness signal, matching
  # salarymap2.csv's CCD_Year for the equivalent K-12 figure.
  #
  # Students_Per_Teacher is NOT stored here -- it's computed on the fly in
  # app.R's map_he (Enrollment / Faculty_Count), the same way map_k12
  # already computes it from Enrollment / Teachers_Total_FTE rather than
  # storing a derived ratio in salarymap2.csv.
  salarymap <- read.csv(file.path("Wy_Ed_Jobs", "salarymap.csv"), fileEncoding = "UTF-8") %>%
    select(-any_of(c("Enrollment", "Enrollment_Year"))) %>%
    left_join(he_enrollment, by = "Name")
  write.csv(salarymap, file.path("Wy_Ed_Jobs", "salarymap.csv"), row.names = FALSE)
} else {
  message("IPEDS fall enrollment fetch failed -- leaving salarymap.csv untouched this run.")
}

# Written as its own read-modify-write against the just-updated file above
# (not folded into the same conditional block) so a trend-fetch failure
# alone can't blank out last week's good Enrollment_Change_Pct values --
# same "leave it alone, don't blank it out" behavior every other salary/
# staffing chunk in this pipeline already has on a failed fetch.
if (nrow(he_enrollment_trend) > 0) {
  salarymap <- read.csv(file.path("Wy_Ed_Jobs", "salarymap.csv"), fileEncoding = "UTF-8") %>%
    select(-any_of("Enrollment_Change_Pct")) %>%
    left_join(he_enrollment_trend, by = "Name")
  write.csv(salarymap, file.path("Wy_Ed_Jobs", "salarymap.csv"), row.names = FALSE)
} else {
  message("IPEDS fall enrollment trend fetch failed -- leaving salarymap.csv's Enrollment_Change_Pct untouched this run.")
}
```

### Higher ed institution Pell Grant recipient share, from the US Dept. of Education's Federal Student Aid office via the Urban Institute's Education Data Portal API
```{r fsa he pell share data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("ipeds_salary_scraper.R")     # fsa_pell_scraper.R reuses fetch_ipeds_directory_paginated()/IPEDS_UNITID_MAP from here
source("ipeds_enrollment_scraper.R") # ...and fetch_ipeds_wy_enrollment_for_year()/parse_ipeds_he_enrollment() from here
source("fsa_pell_scraper.R")

he_pell_share <- safe_scrape(
  "FSA Pell Grant recipient share (WY)",
  scrape_fn = fetch_ipeds_he_pell_share,
  expected_cols = c("Name", "Pell_Recipient_Share", "Pell_Year")
)

if (nrow(he_pell_share) > 0) {
  # No "last updated" timestamp -- same reasoning as every other salary/
  # staffing chunk. Pell_Year is the real freshness signal (and, since FSA
  # lags IPEDS by a couple of years, will typically read a year or more
  # older than Enrollment_Year/Salary_Year above -- expected, not a bug).
  salarymap <- read.csv(file.path("Wy_Ed_Jobs", "salarymap.csv"), fileEncoding = "UTF-8") %>%
    select(-any_of(c("Pell_Recipient_Share", "Pell_Year"))) %>%
    left_join(he_pell_share, by = "Name")
  write.csv(salarymap, file.path("Wy_Ed_Jobs", "salarymap.csv"), row.names = FALSE)
} else {
  message("FSA Pell Grant recipient share fetch failed -- leaving salarymap.csv untouched this run.")
}
```

### Higher ed institution county-level context (income, rent, mining/energy employment share, population trend), from the Census Bureau's ACS 5-Year Estimates
```{r census county context data he, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("census_acs_scraper.R")

# Reuses the exact same fetch_census_county_context() pipeline as the K-12
# chunk earlier in this file -- salarymap.csv's County column (hand-
# maintained the same way Latitude/Longitude already are, added
# 2026-08-06 -- each of Wyoming's 9 public HE institutions is a single
# campus with one real home county) was the only thing missing to make
# this join possible; no new scraper needed. Fetched independently rather
# than reusing the K-12 chunk's `county_context` variable, matching every
# other chunk in this file being self-contained and re-runnable on its
# own -- this data changes at most once a year, so a second cheap fetch
# costs nothing.
county_context_he <- safe_scrape(
  "Census ACS county context for HE institutions (WY)",
  scrape_fn = fetch_census_county_context,
  expected_cols = c("County", "Median_Household_Income", "Median_Gross_Rent",
                     "Population", "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct")
)

if (nrow(county_context_he) > 0) {
  # select(-any_of(...)) drops last run's copy first so a re-run doesn't
  # produce .x/.y duplicates, only reached on a successful fetch -- same
  # "never blank out last week's good values on a failed fetch" pattern
  # the K-12 census chunk uses.
  salarymap <- read.csv(file.path("Wy_Ed_Jobs", "salarymap.csv"), fileEncoding = "UTF-8") %>%
    select(-any_of(c("Median_Household_Income", "Median_Gross_Rent", "Population",
                      "ACS_Year", "Mining_Employment_Share", "Population_Change_Pct"))) %>%
    left_join(county_context_he, by = "County")
  write.csv(salarymap, file.path("Wy_Ed_Jobs", "salarymap.csv"), row.names = FALSE)
} else {
  message("Census ACS county context fetch failed -- leaving salarymap.csv untouched this run.")
}
```
