---
title: "R Job Scrape"
author: "Mark Perkins"
date: "2025-09-18"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("k12_he_classification.R")
```
# This Markdown file contains all the code to scrape data from Wyoming's k12 and higher education job postings

## Part 1: Wyoming K12 Data

### Loop K12 data pulled from all districts that use applitrack
```{r loop with district sites on applitrack, message=FALSE, warning=FALSE, echo=TRUE}
# Load required libraries
library(rvest)
library(RSelenium)
library(dplyr)
library(readr)
source("scrape_helpers.R")

# Read the CSV file
csv_file <- "Frontline_Job_Links.csv"
job_links <- read_csv(csv_file)

# Start RSelenium with Firefox browser
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

# Iterate over each row in the CSV file. Each district's scrape is wrapped
# in its own tryCatch and logged individually (there isn't one safe_scrape()
# call for this chunk since it covers many districts, not one source) -- one
# district's dead site/changed selector no longer aborts every other
# district's scrape for the week, and every district's outcome (ok/empty/
# error) is recorded to scrape_log.csv instead of only a transient cat().
all_jobs_data <- tryCatch({
  results <- list()

  for (i in 1:nrow(job_links)) {
    url <- job_links$JobSite[i]
    school_district <- job_links$`School District`[i]  # Extract the School District

    jobs_data <- tryCatch({
      # Load the page
      remDr$navigate(url)

      # Wait for dynamic content to load (adjust time as needed)
      Sys.sleep(10)  # Adjust as needed based on page loading time

      # Get page source and parse with rvest
      page_source <- remDr$getPageSource()[[1]]
      soup <- read_html(page_source)

      # Extract job listings
      list_items <- soup %>%
        html_nodes("ul.postingsList")

      # Debug: print the number of job listings found
      cat("Number of job listings found at", url, ":", length(list_items), "\n")

      if (length(list_items) == 0) {
        # If no jobs found, create a placeholder row
        log_scrape_result(school_district, status = "empty", n_rows = 0)
        list(list(
          title = "No jobs",
          position = NA,
          position2 = NA,
          date_posted = NA,
          location = NA,
          closing_date = NA,
          school_district = school_district
        ))
      } else {
        # Iterate over each job listing
        district_jobs <- list()
        for (item in list_items) {
          current_job <- list()

          # Extract job title
          current_job$title <- item %>%
            html_node("table.title td#wrapword") %>%
            html_text(trim = TRUE)

          # Extract additional details
          labels <- item %>%
            html_nodes("li span.label") %>%
            html_text(trim = TRUE)

          values <- item %>%
            html_nodes("li span.normal") %>%
            html_text(trim = TRUE)

          # Match labels and values
          j <- 1
          for (k in seq_along(labels)) {
            label <- labels[k]
            if (label == "Position Type:") {
              current_job$position <- values[j]
              if (j + 1 <= length(values) && !grepl(":", values[j + 1])) {
                current_job$position2 <- values[j + 1]
                j <- j + 1
              } else {
                current_job$position2 <- NULL
              }
            } else if (label == "Date Posted:") {
              current_job$date_posted <- values[j]
            } else if (label == "Location:") {
              current_job$location <- values[j]
            } else if (label == "Closing Date:") {
              current_job$closing_date <- values[j]
            }
            j <- j + 1
          }

          # Add the School District information
          current_job$school_district <- school_district

          # Append current job data
          district_jobs <- c(district_jobs, list(current_job))
        }

        log_scrape_result(school_district, status = "ok", n_rows = length(district_jobs))
        district_jobs
      }
    }, error = function(e) {
      message("Applitrack loop: error scraping ", school_district, " (", url, "): ", conditionMessage(e))
      log_scrape_result(school_district, status = "error", n_rows = 0, error_message = conditionMessage(e))
      list(list(
        title = "No jobs",
        position = NA,
        position2 = NA,
        date_posted = NA,
        location = NA,
        closing_date = NA,
        school_district = school_district
      ))
    })

    # Append jobs data for this district to overall results
    results <- c(results, jobs_data)
  }

  results
}, finally = {
  stop_selenium(selenium_session)
})

# Convert list of all job data to data frame
all_jobs_df <- bind_rows(all_jobs_data) %>%
  mutate(
    new_position = if_else(grepl("^\\d", position2), position, position),
    new_position2 = if_else(grepl("^\\d", position2), NA_character_, position2),
    new_date_posted = if_else(grepl("^\\d", position2), position2, date_posted),
    new_location = if_else(grepl("^\\d", position2), date_posted, location),
    new_closing_date = if_else(grepl("^\\d", position2), location, closing_date)
  ) %>%
  select(
    title,
    new_position,
    new_position2,
    new_date_posted,
    new_location,
    new_closing_date,
    school_district
  ) %>%
  rename(
    position = new_position,
    position2 = new_position2,
    date_posted = new_date_posted,
    location = new_location,
    closing_date = new_closing_date
  )

# Join with original job_links for extra metadata
all_jobs_df <- left_join(all_jobs_df, job_links, by = c("school_district" = "School District"))

# Save data frame to CSV file
write.csv(all_jobs_df, "all_job_listings.csv", row.names = FALSE)

```

### Loop k12 data from districts that use Tedd k12
```{r tedk12, message=FALSE, warning=FALSE, echo=TRUE}

# Load required libraries
library(rvest)
library(RSelenium)
library(dplyr)
library(readr)
library(purrr)
source("scrape_helpers.R")

# Read the CSV file containing the URLs
tedjoblinks <- read.csv("tedk12_job_links.csv", stringsAsFactors = FALSE)

# Initialize an empty data frame to store the job data
all_ted_data <- data.frame(
  title = character(),
  date_posted = character(),
  position = character(),
  location = character(),
  url = character(),
  stringsAsFactors = FALSE
)

# Loop through each URL in the CSV file. No Selenium session here (plain
# read_html against a static page), so each URL just needs its own
# tryCatch + log entry -- one dead/changed URL no longer aborts every URL
# after it in the CSV.
for (i in 1:nrow(tedjoblinks)) {
  url <- tedjoblinks$Job.Link[i]  # Using the Job.Link column for URLs

  jobs <- tryCatch({
    # Read the HTML content of the page
    page <- read_html(url)

    # Extract job title, posting date, type, and location
    result <- page %>%
      html_nodes("tr") %>% # Assuming each job is within a <tr> element
      map_df(~{
        title <- .x %>%
          html_node("td:nth-child(1) a") %>%
          html_text(trim = TRUE)

        date_posted <- .x %>%
          html_node("td:nth-child(2)") %>%
          html_text(trim = TRUE)

        position <- .x %>%
          html_node("td:nth-child(3)") %>%
          html_text(trim = TRUE)

        location <- .x %>%
          html_node("td:nth-child(4)") %>%
          html_text(trim = TRUE)

        data.frame(
          title = title,
          date_posted = date_posted,
          position = position,
          location = location,
          url = url,  # Add the URL to the data frame
          stringsAsFactors = FALSE
        )
      })

    log_scrape_result(url, status = if (nrow(result) > 0) "ok" else "empty", n_rows = nrow(result))
    result
  }, error = function(e) {
    message("tedk12: error scraping ", url, ": ", conditionMessage(e))
    log_scrape_result(url, status = "error", n_rows = 0, error_message = conditionMessage(e))
    data.frame(title = character(), date_posted = character(), position = character(),
               location = character(), url = character(), stringsAsFactors = FALSE)
  })

  # Append the jobs data to the all_jobs_data data frame
  all_ted_data <- bind_rows(all_ted_data, jobs)
}

# Remove rows with NA or "Job Title" in the job_title column
all_ted_data <- all_ted_data %>%
  filter(!is.na(title) & title != "Job Title")

all_ted_data<-left_join(all_ted_data, tedjoblinks, by = c("url" = "Job.Link"))


# Save the extracted data to a CSV file
write.csv(all_ted_data, "all_tedk12_job_listings.csv", row.names = FALSE)

```

### Loop k12 data from all districts that use springer school
```{r jobs from spring school, message=FALSE, warning=FALSE, echo=TRUE}

# Load required libraries
library(RSelenium)
library(rvest)
library(dplyr)
library(stringr)
library(lubridate)
library(purrr)
source("scrape_helpers.R")

# ----------------------------
# Start RSelenium
# ----------------------------
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

# ----------------------------
# Read the CSV file containing the URLs
# ----------------------------
springerjoblinks <- read.csv("springer_job_links.csv", stringsAsFactors = FALSE)

# ----------------------------
# Initialize empty data frame
# ----------------------------
all_springer_data <- data.frame(
  title = character(),
  date_posted_text = character(),
  date_posted = as.Date(character()),
  position = character(),
  location = character(),
  url = character(),
  district = character(),
  stringsAsFactors = FALSE
)

# ----------------------------
# Helper functions
# ----------------------------

# Wait for an element to appear
wait_for_element <- function(remDr, css_selector, timeout = 10) {
  for (i in 1:timeout) {
    element <- tryCatch(remDr$findElement(using = "css selector", css_selector), error = function(e) NULL)
    if (!is.null(element)) return(element)
    Sys.sleep(1)
  }
  return(NULL)
}

# Safely extract text
safe_html_text <- function(node) {
  tryCatch(html_text(node, trim = TRUE), error = function(e) NA_character_)
}

# Convert relative dates to actual dates
resolve_relative_date <- function(text, reference_date = Sys.Date()) {
  text <- str_trim(text)
  case_when(
    str_detect(text, regex("^today$", ignore_case = TRUE)) ~ reference_date,
    str_detect(text, regex("^yesterday$", ignore_case = TRUE)) ~ reference_date - days(1),
    str_detect(text, regex("\\d+\\s+days?\\s+ago", ignore_case = TRUE)) ~
      reference_date - days(as.numeric(str_extract(text, "\\d+"))),
    TRUE ~ suppressWarnings(as.Date(str_extract(text, "\\w{3} \\d{2}, \\d{4}"), format = "%b %d, %Y"))
  )
}

# ----------------------------
# Scrape a single URL
# ----------------------------
scrape_jobs <- function(remDr, url) {
  remDr$navigate(url)
  Sys.sleep(3)  # initial load

  # Close pop-up if it exists
  tryCatch({
    close_btn <- remDr$findElement(using = "css selector", "#navigate-away-from-section-dialog-btn-cancel")
    close_btn$clickElement()
  }, error = function(e) NULL)

  # Scroll and click "More Jobs" until fully loaded
  max_attempts <- 30
  attempts <- 0
  last_count <- 0
  buffer_clicks <- 3

  repeat {
    remDr$executeScript("window.scrollTo(0, document.body.scrollHeight);")
    Sys.sleep(1.5)

    page <- read_html(remDr$getPageSource()[[1]])
    jobs_nodes <- html_nodes(page, xpath = "//div[contains(@class, 'card-body')]")
    current_count <- length(jobs_nodes)

    if (current_count == last_count) {
      if (buffer_clicks > 0) {
        buffer_clicks <- buffer_clicks - 1
      } else break
    } else {
      last_count <- current_count
      buffer_clicks <- 3
    }

    # Click "More Jobs" if present
    more_btn <- tryCatch(wait_for_element(remDr, ".pds-secondary-btn"), error = function(e) NULL)
    if (!is.null(more_btn)) {
      more_btn$clickElement()
      Sys.sleep(2)
      attempts <- attempts + 1
    } else break

    if (attempts >= max_attempts) break
  }

  # Extract job info
  months_vec <- c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")
  jobs_data <- map_df(jobs_nodes, ~{
    title <- safe_html_text(html_node(.x, xpath = ".//div[contains(@class, 'card-title')]/div"))
    paragraphs <- html_nodes(.x, "p") %>% map_chr(safe_html_text)

    # Extract position and location by order of <p> elements
    position <- if(length(paragraphs) >= 1) paragraphs[1] else NA_character_
    location <- if(length(paragraphs) >= 2) paragraphs[2] else NA_character_
    date_posted_text <- if(length(paragraphs) >= 3) paragraphs[3] else NA_character_

    date_posted <- resolve_relative_date(date_posted_text)

    tibble(
      title = title,
      position = position,
      location = location,
      date_posted_text = date_posted_text,
      date_posted = date_posted,
      url = url,
      district = NA_character_
    )
  })

  return(jobs_data)
}


# ----------------------------
# Loop through each URL and scrape. Each URL is now wrapped in its own
# tryCatch + log entry -- one dead/changed district site no longer aborts
# every district after it in the CSV.
# ----------------------------
all_springer_data <- tryCatch({
  for (i in 1:nrow(springerjoblinks)) {
    url <- springerjoblinks$`Job.Link`[i]
    message(paste("Processing URL:", url))

    job_data <- tryCatch(scrape_jobs(remDr, url), error = function(e) {
      message("Springer: error scraping ", url, ": ", conditionMessage(e))
      log_scrape_result(url, status = "error", n_rows = 0, error_message = conditionMessage(e))
      NULL
    })

    if (!is.null(job_data) && nrow(job_data) > 0) {
      all_springer_data <- bind_rows(all_springer_data, job_data)
      message(paste("Scraped", nrow(job_data), "jobs from:", url))
      log_scrape_result(url, status = "ok", n_rows = nrow(job_data))
    } else if (!is.null(job_data)) {
      message("No jobs found at:", url)
      log_scrape_result(url, status = "empty", n_rows = 0)
    }
  }
  all_springer_data
}, finally = {
  stop_selenium(selenium_session)
})

# ----------------------------
# Merge with original CSV and clean up
# ----------------------------
all_springer_data <- left_join(all_springer_data, springerjoblinks, by = c("url" = "Job.Link"))

all_springer_data <- all_springer_data %>%
  mutate(date_posted = resolve_relative_date(date_posted_text)) %>%
  dplyr::select(-c(district, date_posted_text))

# ----------------------------
# Save to CSV
# ----------------------------
write.csv(all_springer_data, "all_springer_job_listings.csv", row.names = FALSE)

```

### Combine all the k12 data include a few manual pulls from unique district sites
#### Be sure to update your manually scraped data
#### This will populate your app folder for your Shiny application
```{r combine all the data into one dataframe, echo=TRUE, warning=FALSE, message=FALSE}
library(stringr)
library(tidyverse)
library(dplyr)
library(lubridate)


standardize_date <- function(x) {

  # Convert factor to character safely
  x <- as.character(x)

  # Remove timezone text like "(UTC)"
  x <- str_remove(x, "\\s*\\(.*\\)$")

  # Parse known formats
  parsed <- parse_date_time(
    x,
    orders = c(
      "b d Y h:M p",   # Oct 23 2025 6:00 AM
      "B d Y h:M p",   # October 23 2025 6:00 AM
      "ymd",
      "mdy",
      "dmy",
      "Y-m-d H:M:S"
    ),
    tz = "UTC",
    quiet = TRUE
  )

  as.Date(parsed)
}



frontline<- read.csv("all_job_listings.csv")%>%
  rename(url = JobSite)

frontline<-  dplyr::select(frontline, title, date_posted, position, location, url, school_district)%>%
  rename(District = school_district)

ted<- read.csv("all_tedk12_job_listings.csv")

springer<- read.csv("all_springer_job_listings.csv")

other<- readxl::read_excel("otherjobs.xlsx")

frontline <- frontline %>%
  mutate(date_posted = standardize_date(date_posted))

ted <- ted %>%
  mutate(date_posted = standardize_date(date_posted))

springer <- springer %>%
  mutate(date_posted = standardize_date(date_posted))

other <- other %>%
  mutate(date_posted = standardize_date(date_posted))


combined<- rbind(frontline, ted, springer, other)%>%
  mutate(Archive_Date = Sys.Date())



file_name <- paste0("combined_", Sys.Date(), ".csv")

# Write the data to a CSV file with the new file name
write.csv(combined, file=file.path('Archivek12_Data',file_name))

# Categorize positions in the "position" column of the "combinedclean" dataset.
# classify_k12_position() lives in k12_he_classification.R (sourced above) so
# this week's raw jobs-table classification and the full-archive rebuild
# below can't silently drift apart.

combinedclean <- combined %>%
  mutate(position = classify_k12_position(title)) %>%
  dplyr::select(title, date_posted, position, location, url, District)

write.csv(combinedclean, file=file.path('Wy_Ed_Jobs','combinedclean.csv'))


#Munge the archived data and send files to Shiny
csv_files <- list.files("Archivek12_Data", pattern = "\\.csv$", full.names = TRUE)

combined_k12_data <- csv_files %>%
  lapply(function(file) read.csv(file, colClasses = c("Archive_Date" = "character"))) %>%
  bind_rows() %>%
  select(-X, -date_posted)

combined_k12_data <- combined_k12_data %>%
  mutate(Archive_Date = case_when(
    grepl("/", Archive_Date) ~ as.Date(Archive_Date, format = "%m/%d/%Y"),
    grepl("-", Archive_Date) ~ as.Date(Archive_Date, format = "%Y-%m-%d"),
    TRUE ~ as.Date(NA)  # Corrected this line
  ))

dates <- as.data.frame(unique(combined_k12_data$Archive_Date))


combined_k12_data$Archive_Date <- as.Date(combined_k12_data$Archive_Date)

###################################################
# Create Categories
# position/Category/Broad_Category classification and District name
# canonicalization all live in k12_he_classification.R (sourced in setup)
# so this full-archive rebuild can't drift from the current-week block above.

combinedclean <- combined_k12_data %>%
  mutate(position = classify_k12_position(title)) %>%
  dplyr::select(title, Archive_Date, position, location, url, District)

combinedclean <- combinedclean %>%
  mutate(District = canonicalize_k12_district(District))

k12jobs <- combinedclean %>%
  filter(position == "Teacher")

k12jobs <- k12jobs %>%
  mutate(Category = classify_k12_subject(title))

k12jobs <- k12jobs %>%
  mutate(Broad_Category = classify_k12_broad_category(Category))

write.csv(k12jobs, file=file.path('Wy_Ed_Jobs','k12jobanalysis.csv'))


#Database for all dates by category
# Dedup key is title+location, not title alone: two different schools in the
# same district legitimately post the same generic title (e.g. "Elementary
# Teacher") for two different, real openings; n_distinct(title) alone would
# silently collapse those into a single counted posting.
#
# The Total row is computed as the SUM of the per-district counts below, not
# as its own independent n_distinct() over every district's rows combined.
# Some scrapers fall back to a generic location placeholder (literally the
# string "District") when they can't extract a real school name, and two
# different districts can both produce that same generic title+location
# combination for two genuinely different real postings; deduping across
# district boundaries would silently collapse those into one and undercount
# the Total relative to its own parts.
k12sumdistrict <- k12jobs %>%
  group_by(Broad_Category, Archive_Date, District) %>%
  summarize(
    sum = n_distinct(paste(title, location))
  ) %>%
  ungroup()

k12sum <- k12sumdistrict %>%
  group_by(Broad_Category, Archive_Date) %>%
  summarize(sum = sum(sum)) %>%
  ungroup() %>%
  mutate(District = "Total") %>%
  select(Broad_Category, Archive_Date, District, sum)

Allsum <- bind_rows(k12sum, k12sumdistrict)
write.csv(Allsum, file=file.path('Wy_Ed_Jobs','allsum.csv'))

#Database for all data now by category
k12now <- k12jobs %>%
  filter(Archive_Date == max(Archive_Date))

k12districtnowsum <- k12now %>%
  group_by(Broad_Category, District) %>%
  summarize(
    Sum = n_distinct(paste(title, location))
  ) %>%
  ungroup() %>%
  select(Broad_Category, Sum, District)

k12nowsum <- k12districtnowsum %>%
  group_by(Broad_Category) %>%
  summarize(Sum = sum(Sum)) %>%
  ungroup() %>%
  mutate(District = "Total")

Allnow <- bind_rows(k12nowsum, k12districtnowsum)

write.csv(Allnow, file=file.path('Wy_Ed_Jobs','allnow.csv'))

list<-unique(k12jobs$District)
write.csv(list, "list.csv")
```


## Time to scrape Wyoming Higher Education Data
### This chunk scrapes LCCC's data
```{r Get Jobs from LCCC, message=FALSE, warning=FALSE, echo=TRUE}

library(rvest)
library(RSelenium)
library(dplyr)
source("scrape_helpers.R")

# Start RSelenium with Firefox browser
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

all_jobs_raw <- tryCatch({
  safe_scrape(
    "Laramie County Community College",
    scrape_fn = function() {
      # Function to scrape job postings from a given page URL
      scrape_jobs <- function(url) {
        remDr$navigate(url)

       # Scroll to bottom once
      remDr$executeScript("window.scrollTo(0, document.body.scrollHeight);")

      # Wait up to ~8 seconds for all job elements to appear
      for(i in 1:16) {     # 16 x 0.5 sec = 8 sec total
        job_nodes <- remDr$findElements(using = "css selector",
                                        value = ".item-details-link")
        if(length(job_nodes) >= 30) break
        Sys.sleep(0.5)
      }


        # Re-fetch the page after waiting for all jobs to load
        page_source <- remDr$getPageSource()[[1]]
        soup <- read_html(page_source)

        # Safely try to fetch job titles, links, locations, and posted dates
        job_titles <- tryCatch({
          soup %>% html_nodes(".item-details-link") %>% html_text(trim = TRUE)
        }, error = function(e) character(0))

        job_links <- tryCatch({
          soup %>% html_nodes(".item-details-link") %>% html_attr("href") %>%
            paste0("https://www.governmentjobs.com/careers/lcccwy?page=", .)
        }, error = function(e) character(0))

        # **Update to capture the Location** correctly for all jobs, including the last one
        job_location <- tryCatch({
          soup %>% html_nodes(".list-meta li:nth-child(1)") %>% html_text(trim = TRUE)
        }, error = function(e) character(0))


        posted_date <- tryCatch({
          soup %>% html_nodes(".list-entry-starts span") %>% html_text(trim = TRUE)
        }, error = function(e) character(0))

        # Ensure all vectors have the same length
        max_length <- max(length(job_titles), length(job_links), length(job_location), length(posted_date))

        job_titles <- c(job_titles, rep(NA, max_length - length(job_titles)))
        job_links <- c(job_links, rep(NA, max_length - length(job_links)))
        job_location <- c(job_location, rep(NA, max_length - length(job_location)))
        posted_date <- c(posted_date, rep(NA, max_length - length(posted_date)))

        # Create dataframe
        jobs_df <- data.frame(
          Title = job_titles,
          Location = job_location,
          Link = job_links,
          Posted_Date = posted_date,
          stringsAsFactors = FALSE
        )

        return(jobs_df)
      }

      # Scrape multiple pages
      all_jobs <- list()

      page <- 1
      repeat {
        url <- paste0("https://www.governmentjobs.com/careers/lcccwy?page=", page)
        cat("Scraping:", url, "\n")

        jobs_df <- tryCatch({
          scrape_jobs(url)
        }, error = function(e) {
          cat("Error scraping page", page, ":", e$message, "\n")
          return(data.frame())
        })

        if (all(is.na(jobs_df$Title)) || nrow(jobs_df) == 0) {
          cat("No job titles found on page", page, ". Assuming end of listings.\n")
          break
        } else {
          all_jobs[[length(all_jobs) + 1]] <- jobs_df
          cat("Scraped page", page, "\n")
          page <- page + 1  # Don't forget to increment the page!
        }

        Sys.sleep(1)  # Be nice to the server
      }

      bind_rows(all_jobs)
    },
    expected_cols = c("Title", "Location", "Link", "Posted_Date")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Combine and clean
lccc <- all_jobs_raw %>%
  mutate(Institution = "Laramie County Community College") %>%
  distinct(Title, .keep_all = TRUE)

# Cleanup and print results
lccc <- lccc %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(lccc)

```

### This pulls data from Casper College
```{r casper college, message=FALSE, warning=FALSE, echo=TRUE}
library(rvest)
library(RSelenium)
library(dplyr)
source("scrape_helpers.R")

# Define the URLs for page 1 and page 2
urls <- c(
  "https://www.schooljobs.com/careers/caspercollege",
  "https://www.schooljobs.com/careers/caspercollege?page=2"
)

# Start RSelenium with Firefox browser
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

casper_raw <- tryCatch({
  safe_scrape(
    "Casper College",
    scrape_fn = function() {
      casper <- data.frame()

      # Loop over both pages to scrape data; one page erroring doesn't lose the other.
      for (url in urls) {
        page_jobs <- tryCatch({
          remDr$navigate(url)
          Sys.sleep(10)  # Wait for dynamic content

          soup <- read_html(remDr$getPageSource()[[1]])

          job_titles <- soup %>%
            html_nodes(".item-details-link") %>%
            html_text(trim = TRUE)

          job_links <- soup %>%
            html_nodes(".item-details-link") %>%
            html_attr("href") %>%
            paste0("https://www.schooljobs.com/careers/caspercollege", .)

          # Extract job locations
          job_locations <- soup %>%
            html_nodes(".list-meta li:nth-child(1)") %>%
            html_text(trim = TRUE)

          if (length(job_locations) == 0) {
            job_locations <- rep(NA, length(job_titles))
          }

          # Extract posted date text (RELATIVE -- keep as-is)
          Posted_Date <- soup %>%
            html_nodes(".list-entry-starts span") %>%
            html_text(trim = TRUE)

          if (length(job_titles) == 0) {
            data.frame(
              Title = "No Jobs",
              Location = NA,
              Posted_Date = NA,
              Institution = "Casper College",
              Link = url,
              stringsAsFactors = FALSE
            )
          } else {
            data.frame(
              Title = job_titles,
              Location = job_locations,
              Posted_Date = Posted_Date,
              Institution = "Casper College",
              Link = job_links,
              stringsAsFactors = FALSE
            )
          }
        }, error = function(e) {
          message("Casper College: error scraping ", url, ": ", conditionMessage(e))
          data.frame(Title = "No Jobs", Location = NA, Posted_Date = NA,
                     Institution = "Casper College", Link = url, stringsAsFactors = FALSE)
        })

        casper <- rbind(casper, page_jobs)
      }

      # Remove duplicates
      unique(casper)
    },
    expected_cols = c("Title", "Location", "Posted_Date", "Institution", "Link")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Final column order & cleanup
casper <- casper_raw %>%
  select(Title, Location, Posted_Date, Institution, Link) %>%
  filter(Title != "No Jobs")

# Print results
print(casper)

```


### This pulls jobs data from Western Wyoming
```{r western wyoming, echo=TRUE, message=FALSE, warning=FALSE}
library(rvest)
library(RSelenium)
library(dplyr)
library(stringr)
source("scrape_helpers.R")

#Convert date to days, weeks, more than 30 days
convert_date_to_relative <- function(date_chr) {
  date_parsed <- as.Date(date_chr, format = "%m/%d/%Y")

  if (is.na(date_parsed)) return(NA_character_)

  days_ago <- as.integer(Sys.Date() - date_parsed)

  if (days_ago < 1) {
    "Posted today"
  } else if (days_ago == 1) {
    "Posted 1 day ago"
  } else if (days_ago < 7) {
    paste("Posted", days_ago, "days ago")
  } else if (days_ago < 14) {
    "Posted 1 week ago"
  } else if (days_ago < 21) {
    "Posted 2 weeks ago"
  } else if (days_ago < 28) {
    "Posted 3 weeks ago"
  } else if (days_ago < 35) {
    "Posted 4 weeks ago"
  } else {
    "Posted more than 30 days ago"
  }
}


# Start RSelenium. NOTE: like Eastern Wyoming originally was, this scraper is
# still hardcoded to pages 1-2 (lapply(1:2, ...)) rather than paginating
# until an empty page -- that specific rewrite wasn't in this pass's scope,
# flagging it here as the same class of risk Eastern had.
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

all_jobs_raw <- tryCatch({
  safe_scrape(
    "Western Wyoming Community College",
    scrape_fn = function() {
      extract_jobs <- function(page_url) {
        remDr$navigate(page_url)
        Sys.sleep(5)  # allow full page load

        page_source <- remDr$getPageSource()[[1]]
        soup <- read_html(page_source)

        jobs <- soup %>% html_nodes("div.job-item.job-item-posting")
        if(length(jobs) == 0) return(NULL)

        job_list <- lapply(jobs, function(job) {
          # Title and Link
          title_node <- job %>% html_node("div.col-md-4.job-title h3 a")
          Title <- title_node %>% html_text(trim = TRUE)
          Link  <- paste0("https://wwccwy.peopleadmin.com", title_node %>% html_attr("href"))

          # Right column text (single string)
          right_text <- job %>% html_node("div.col-md-8") %>% html_text(trim = TRUE)

          # Posted_Date: first occurrence of MM/DD/YYYY
          raw_date <- str_extract(right_text, "\\d{2}/\\d{2}/\\d{4}")
          Posted_Date <- convert_date_to_relative(raw_date)


          # Location: last non-empty line that is NOT a date or code
          lines <- str_split(right_text, "\\n")[[1]] %>% str_trim()
          non_date <- lines[!str_detect(lines, "\\d{2}/\\d{2}/\\d{4}")]
          non_empty <- non_date[nzchar(non_date)]
          Location <- if(length(non_empty) > 0) tail(non_empty, 1) else NA

          data.frame(
            Title = Title,
            Location = Location,
            Posted_Date = Posted_Date,
            Link = Link,
            stringsAsFactors = FALSE
          )
        })

        do.call(rbind, job_list)
      }

      # Scrape pages 1 and 2
      do.call(rbind, lapply(1:2, function(p) {
        url <- paste0("https://wwccwy.peopleadmin.com/postings/search?page=", p)
        tryCatch(extract_jobs(url), error = function(e) {
          message("Western Wyoming Community College: error scraping page ", p, ": ", conditionMessage(e))
          NULL
        })
      }))
    },
    expected_cols = c("Title", "Location", "Posted_Date", "Link")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Add Institution column
western <- all_jobs_raw %>% mutate(Institution = "Western Wyoming Community College")%>%
  dplyr::select(Title, Location, Posted_Date, Institution, Link)

# Save CSV
write.csv(western, "WWCC_job_listings.csv", row.names = FALSE)

# Print
print(western)

```


### This pulls data from Central Wyoming college
```{r central wyoming, message=FALSE, echo=TRUE, warning=FALSE}
library(rvest)
library(RSelenium)
library(dplyr)
library(purrr)
source("scrape_helpers.R")

# Start RSelenium with Firefox browser
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

all_jobs_raw <- tryCatch({
  safe_scrape(
    "Central Wyoming College",
    scrape_fn = function() {
      # Function to extract job postings from a page
      extract_jobs <- function(page_url) {
        remDr$navigate(page_url)
        Sys.sleep(10)  # Adjust as needed based on page loading time

        page_source <- remDr$getPageSource()[[1]]
        soup <- read_html(page_source)

        job_titles <- soup %>%
          html_nodes(".list-item .item-details-link") %>%
          html_text(trim = TRUE)

        job_dates <- soup %>%
          html_nodes(".list-published .list-entry-starts span") %>%
          html_text(trim = TRUE)

        job_locations <- soup %>%
          html_nodes(".list-item ul.list-meta li:nth-child(1)") %>%
          html_text(trim = TRUE)

        data.frame(
          Title = job_titles,
          Location = job_locations,
          Posted_Date = job_dates,
          stringsAsFactors = FALSE
        )
      }

      all_jobs <- data.frame()
      for (page in 1:3) {
        # NB: no space before `page` here -- the original had "?page= "
        # (with a trailing space before the number), which could send pages
        # 2-3 a malformed query string and silently re-scrape page 1.
        page_url <- if (page == 1) {
          "https://www.schooljobs.com/careers/cwc"
        } else {
          paste0("https://www.schooljobs.com/careers/cwc?page=", page)
        }

        page_jobs <- tryCatch(extract_jobs(page_url), error = function(e) {
          message("Central Wyoming College: error scraping page ", page, ": ", conditionMessage(e))
          data.frame()
        })

        if (nrow(page_jobs) > 0) {
          all_jobs <- bind_rows(all_jobs, page_jobs)
          cat("Scraped page", page, "\n")
        } else {
          cat("No data found on page", page, "\n")
        }
      }
      all_jobs
    },
    expected_cols = c("Title", "Location", "Posted_Date")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Add the current date to the dataframe
central <- all_jobs_raw %>%
  mutate(Institution = "Central Wyoming College")%>%
  mutate(Link = "https://www.schooljobs.com/careers/cwc")

# Print the dataframe
print(central)

```

### This pulls jobs data from Eastern Wyoming college
```{r Eastern, message=FALSE, warning=FALSE, echo=TRUE}
library(rvest)
library(RSelenium)
library(dplyr)
library(stringr)
library(lubridate)
library(purrr)
source("scrape_helpers.R")
source("eastern_wyoming_scraper.R")

convert_to_relative_date <- function(date_obj, reference_date = Sys.Date()) {
  diff_days <- as.numeric(difftime(reference_date, date_obj, units = "days"))

  if(is.na(diff_days)) return(NA_character_)
  else if(diff_days == 0) return("Today")
  else if(diff_days == 1) return("Yesterday")
  else if(diff_days < 7) return(paste(diff_days, "days ago"))
  else if(diff_days < 30) return(paste(round(diff_days/7), "weeks ago"))
  else return("More than 30 days ago")
}

# Start RSelenium. Pagination (until an empty page), per-job Open Date
# lookup, and per-page/per-job error handling all live in
# eastern_wyoming_scraper.R -- previously this chunk was hardcoded to
# "scrape first 2 pages" with no error handling anywhere, so a single dead
# link or a page beyond #2 either got silently dropped or crashed the whole
# chunk. tryCatch/finally guarantees the Selenium session is closed even if
# something throws (on.exit doesn't reliably fire at a knitr chunk's
# top level the way it would inside a function).
selenium_session <- start_selenium()

all_jobs <- tryCatch({
  safe_scrape(
    "Eastern Wyoming Community College",
    scrape_fn = function() scrape_eastern_wyoming(selenium_session$remDr),
    expected_cols = c("Title", "Link", "Posted_Date")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Add metadata and convert Posted_Date to relative
eastern <- all_jobs %>%
  mutate(
    Location = "Eastern Wyoming Campus",
    Institution = "Eastern Wyoming Community College",
    Posted_Date = map_chr(as.Date(Posted_Date), convert_to_relative_date)) %>%
  dplyr::select(Title, Location, Posted_Date, Institution, Link)%>%
  distinct()

print(eastern)
```

### This pulls data Gillette college
```{r gillette, message=FALSE, echo=TRUE, warning=FALSE}
library(rvest)
library(RSelenium)
library(dplyr)
source("scrape_helpers.R")

# Start RSelenium with Firefox browser
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

all_jobs_raw <- tryCatch({
  safe_scrape(
    "Gillette College",
    scrape_fn = function() {
      # Function to extract job postings from a page
      extract_jobs <- function(page_url) {
        remDr$navigate(page_url)
        Sys.sleep(10)  # Adjust as needed based on page loading time

        page_source <- remDr$getPageSource()[[1]]
        soup <- read_html(page_source)

        job_titles <- soup %>%
          html_nodes(".list-item .item-details-link") %>%
          html_text(trim = TRUE)

        job_dates <- soup %>%
          html_nodes(".list-published .list-entry-starts span") %>%
          html_text(trim = TRUE)

        job_locations <- soup %>%
          html_nodes(".list-item ul.list-meta li:nth-child(1)") %>%
          html_text(trim = TRUE)

        data.frame(
          Title = job_titles,
          Location = job_locations,
          Posted_Date = job_dates,
          stringsAsFactors = FALSE
        )
      }

      all_jobs <- data.frame()
      for (page in 1:5) {
        # NB: no space before `page` here -- the original had "?page= "
        # (with a trailing space before the number), which could send pages
        # 2-5 a malformed query string and silently re-scrape page 1.
        page_url <- if (page == 1) {
          "https://www.schooljobs.com/careers/gillettecollege"
        } else {
          paste0("https://www.schooljobs.com/careers/gillettecollege?page=", page)
        }

        page_jobs <- tryCatch(extract_jobs(page_url), error = function(e) {
          message("Gillette College: error scraping page ", page, ": ", conditionMessage(e))
          data.frame()
        })

        if (nrow(page_jobs) > 0) {
          all_jobs <- bind_rows(all_jobs, page_jobs)
          cat("Scraped page", page, "\n")
        } else {
          cat("No data found on page", page, "\n")
        }
      }
      all_jobs
    },
    expected_cols = c("Title", "Location", "Posted_Date")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Add the current date to the dataframe
gillette <- all_jobs_raw %>%
  mutate(Institution = "Gillette College")%>%
  mutate(Link = "https://www.schooljobs.com/careers/gillettecollege")

print(gillette)

```

### This pulls data from Sheridan College
```{r sheridan, echo=TRUE, message=FALSE, warning=FALSE}
library(rvest)
library(RSelenium)
library(dplyr)
library(purrr)
library(stringr)
library(lubridate)
source("scrape_helpers.R")

# Function to convert date to relative format
convert_to_relative_date <- function(date_obj, reference_date = Sys.Date()) {
  diff_days <- as.numeric(difftime(reference_date, date_obj, units = "days"))

  if(is.na(diff_days)) return(NA_character_)
  else if(diff_days == 0) return("Today")
  else if(diff_days == 1) return("Yesterday")
  else if(diff_days < 7) return(paste(diff_days, "days ago"))
  else if(diff_days < 30) return(paste(round(diff_days/7), "weeks ago"))
  else return("More than 30 days ago")
}

# Start RSelenium
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

all_jobs_raw <- tryCatch({
  safe_scrape(
    "Sheridan College",
    scrape_fn = function() {
      extract_jobs <- function(page_url) {
        remDr$navigate(page_url)
        Sys.sleep(10)  # allow full load

        soup <- read_html(remDr$getPageSource()[[1]])

        # Get job titles and links
        title_nodes <- soup %>% html_nodes(".col-md-4.job-title h3 a")
        Titles <- title_nodes %>% html_text(trim = TRUE)
        Links  <- title_nodes %>% html_attr("href") %>% paste0("https://jobs.sheridan.edu", .)

        if(length(Titles) == 0) return(NULL)

        job_list <- lapply(seq_along(Titles), function(i) {
          # Visit detail page for the posting; one dead link/parse failure
          # falls back to a missing Posted_Date instead of aborting every
          # other job on this and later pages.
          tryCatch({
            remDr$navigate(Links[i])
            Sys.sleep(5)  # wait for detail page

            detail_page <- read_html(remDr$getPageSource()[[1]])

            # Extract "Job Posting Date"
            posted_date_text <- detail_page %>%
              html_nodes("th") %>%
              { .[str_detect(html_text(.), "Job Posting Date")] } %>%
              html_node(xpath = "following-sibling::td") %>%
              html_text(trim = TRUE)

            Posted_Date <- if(length(posted_date_text) == 1) mdy(posted_date_text) else NA

            data.frame(
              Title = Titles[i],
              Link = Links[i],
              Posted_Date = Posted_Date,
              stringsAsFactors = FALSE
            )
          }, error = function(e) {
            message("Sheridan College: error fetching detail for '", Titles[i], "': ", conditionMessage(e))
            data.frame(Title = Titles[i], Link = Links[i], Posted_Date = as.Date(NA), stringsAsFactors = FALSE)
          })
        })

        do.call(rbind, job_list)
      }

      # Scrape first 3 pages (adjust if needed); one bad page doesn't drop the others.
      all_jobs_list <- lapply(1:3, function(p) {
        url <- paste0("https://jobs.sheridan.edu/postings/search?page=", p)
        tryCatch(extract_jobs(url), error = function(e) {
          message("Sheridan College: error scraping page ", p, ": ", conditionMessage(e))
          NULL
        })
      })

      # Remove NULL pages
      all_jobs_list <- all_jobs_list[!sapply(all_jobs_list, is.null)]
      do.call(rbind, all_jobs_list)
    },
    expected_cols = c("Title", "Link", "Posted_Date")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Add metadata and convert to relative date
sheridan <- all_jobs_raw %>%
  mutate(
    Location = "Sheridan College Campus",
    Institution = "Sheridan College",
    Posted_Date = map_chr(Posted_Date, convert_to_relative_date))%>%
  dplyr::select(Title, Location, Posted_Date, Institution, Link)%>%
  distinct()

print(sheridan)

```

### This pulls data from Northwest College
```{r Northwest, message=FALSE, warning=FALSE, echo=TRUE}
library(rvest)
library(RSelenium)
library(lubridate)
library(dplyr)
library(purrr)
source("scrape_helpers.R")

convert_to_relative_date <- function(date_str, reference_date = Sys.Date()) {
  # Convert to Date
  actual_date <- mdy(date_str)  # assumes MM/DD/YYYY
  diff_days <- as.numeric(difftime(reference_date, actual_date, units = "days"))

  # Convert to relative format
  if(is.na(diff_days)) return(NA_character_)
  else if(diff_days == 0) return("Today")
  else if(diff_days == 1) return("Yesterday")
  else if(diff_days < 7) return(paste(diff_days, "days ago"))
  else if(diff_days < 30) return(paste(round(diff_days/7), "weeks ago"))
  else return("More than 30 days ago")
}

# Start RSelenium with Firefox browser. Scrape wrapped in safe_scrape() so a
# failure here is logged and degrades to "Northwest missing this week"
# instead of halting every chunk after it.
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

all_jobs_raw <- tryCatch({
  safe_scrape(
    "Northwest College",
    scrape_fn = function() {
      # Function to extract job postings from a page
      extract_jobs <- function(page_url) {
        remDr$navigate(page_url)
        Sys.sleep(10)  # Adjust as needed based on page loading time

        page_source <- remDr$getPageSource()[[1]]
        soup <- read_html(page_source)

        job_titles <- soup %>%
          html_nodes(".row.row-table .job-title h3 a") %>%
          html_text()

        posted_dates <- soup %>%
          html_nodes(".row.row-table .tbody-cell.col-3:nth-child(1)") %>%
          html_text()

        locations <- soup %>%
          html_nodes(".row.row-table .tbody-cell.col-3:nth-child(3)") %>%
          html_text()

        data.frame(
          Title = job_titles,
          Posted_Date = posted_dates,
          Location = locations,
          stringsAsFactors = FALSE
        )
      }

      all_jobs <- data.frame()
      for (page in 1:3) {
        page_url <- paste0("https://northwestcollege.simplehire.com/postings/search?page=", page)
        page_jobs <- tryCatch(extract_jobs(page_url), error = function(e) {
          message("Northwest College: error scraping page ", page, ": ", conditionMessage(e))
          data.frame()
        })

        if (nrow(page_jobs) > 0) {
          all_jobs <- bind_rows(all_jobs, page_jobs)
          cat("Scraped page", page, "\n")
        } else {
          cat("No data found on page", page, "\n")
        }
      }
      all_jobs
    },
    expected_cols = c("Title", "Posted_Date", "Location")
  )
}, finally = {
  stop_selenium(selenium_session)
})

northwest <- all_jobs_raw %>%
  mutate(Institution = "Northwest College") %>%
  mutate(Link = "https://northwestcollege.simplehire.com/postings/search?page=") %>%
  select(Title, Location, Posted_Date, Institution, Link)

northwest <- northwest %>%
  mutate(
    Posted_Date = map_chr(Posted_Date, convert_to_relative_date)
  )

# Print the dataframe
print(northwest)

```



### This pulls data from the University of Wyoming
```{r university of Wyoming}
library(RSelenium)
library(dplyr)
library(purrr)
library(lubridate)
source("scrape_helpers.R")

# Function to convert dates to relative format
convert_to_relative_date <- function(date_str, reference_date = Sys.Date()) {
  if(is.na(date_str) || date_str == "") return(NA_character_)

  actual_date <- mdy(date_str)  # MM/DD/YYYY
  diff_days <- as.numeric(difftime(reference_date, actual_date, units = "days"))

  if(is.na(diff_days)) return(NA_character_)
  else if(diff_days == 0) return("Today")
  else if(diff_days == 1) return("Yesterday")
  else if(diff_days < 7) return(paste(diff_days, "days ago"))
  else if(diff_days < 30) return(paste(round(diff_days/7), "weeks ago"))
  else return("More than 30 days ago")
}

url <- "https://eeik.fa.us2.oraclecloud.com/hcmUI/CandidateExperience/en/sites/CX_1/requisitions?"

# Start RSelenium. The scrape itself is wrapped in safe_scrape() so a
# selector/timeout failure here doesn't halt every chunk after it in the
# knit, and tryCatch/finally guarantees the session is closed either way.
selenium_session <- start_selenium()
remDr <- selenium_session$remDr

UW_raw <- tryCatch({
  safe_scrape(
    "University of Wyoming",
    scrape_fn = function() {
      remDr$navigate(url)
      Sys.sleep(5)  # wait for initial load

      # Scroll to load all jobs
      scroll_pause_time <- 3
      last_height <- remDr$executeScript("return document.body.scrollHeight")[[1]]

      repeat {
        remDr$executeScript("window.scrollTo(0, document.body.scrollHeight);")
        Sys.sleep(scroll_pause_time)
        new_height <- remDr$executeScript("return document.body.scrollHeight")[[1]]
        if (new_height == last_height) break
        last_height <- new_height
      }

      # Extract job titles
      titles_elems <- remDr$findElements(using = 'css selector', ".job-tile__title")
      job_titles <- sapply(titles_elems, function(x) x$getElementText()) %>% unlist()

      # Extract job locations
      locations_elems <- remDr$findElements(using = 'css selector', "span[data-bind='html: primaryLocation']")
      job_locations <- sapply(locations_elems, function(x) x$getElementText()) %>% unlist()

      # Extract posted dates
      dates_elems <- remDr$findElements(
        using = 'css selector',
        "div.job-list-item__job-info-label--posting-date + div div.job-list-item__job-info-value"
      )
      posted_dates <- sapply(dates_elems, function(x) x$getElementText()) %>% unlist()

      data.frame(
        Title = job_titles,
        Location = job_locations,
        Posted_Date = posted_dates,
        stringsAsFactors = FALSE
      )
    },
    expected_cols = c("Title", "Location", "Posted_Date")
  )
}, finally = {
  stop_selenium(selenium_session)
})

# Convert Posted_Date to relative format
UW <- UW_raw %>%
  mutate(
    Institution = "University of Wyoming",
    Link = url,
    Posted_Date = map_chr(Posted_Date, convert_to_relative_date)
  ) %>%
  select(Title, Location, Posted_Date, Institution, Link)

# Print results
print(UW)

```

### Combine all the Higher Education data
#### This will populate your app folder for your Shiny application
```{r munge he data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(writexl)
library(tidyverse)
library(readxl)

# Combine all datasets
hedata <- rbind(lccc, casper, western, central, eastern, gillette, sheridan, northwest, UW)

hedata$Posted_Date<- as.character(hedata$Posted_Date)

hedata <- hedata %>%
  mutate(Archive_Date = Sys.Date())

# Save data with a time stamp
file_name <- paste0("hedata_", Sys.Date(), ".xlsx")

write_xlsx(hedata, path = file_name)

write_xlsx(hedata, path = file.path("Archived_HE_Data", file_name))
write_xlsx(hedata, path = file.path("Wy_Ed_Jobs", "hedata.xlsx"))

csv_files <- list.files("Archived_HE_Data", pattern = "\\.xlsx$", full.names = TRUE)

combined_HE_data <- csv_files %>%
  lapply(read_xlsx) %>%   
  bind_rows()

combined_HE_data$Archive_Date <- as.Date(combined_HE_data$Archive_Date)

# Fix historical institution-name typos before anything downstream keys off
# Institution, so a college's history doesn't silently split across two
# spellings (see canonicalize_he_institution() in k12_he_classification.R).
combined_HE_data <- combined_HE_data %>%
  mutate(Institution = canonicalize_he_institution(Institution))

# Job_Type/Category classification lives in k12_he_classification.R (sourced
# in setup). Adjunct/pooled titles get their own Job_Type, separate from
# "Instructor/Teacher/Faculty", so a standing adjunct-pool posting isn't
# counted the same as full-time faculty hiring.
combined_cat <- combined_HE_data %>%
  mutate(Job_Type = classify_he_job_type(Title))

facultydata <- combined_cat %>%
  filter(Job_Type == "Instructor/Teacher/Faculty") %>%
  mutate(Category = classify_he_faculty_category(Title))
write.csv(facultydata, "facultydata.csv")
hesum <- facultydata %>%
  group_by(Category, Archive_Date) %>%
  summarize(
    sum = n()
  ) %>%
  ungroup()%>%
  mutate(Institution = "Total")%>%
  select(Category, Archive_Date, Institution, sum)

hesuminst<- facultydata%>%
  group_by(Category, Archive_Date, Institution)%>%
  summarise(
    sum = n()
  )%>%
  ungroup()

Allsum_he<-rbind(hesum, hesuminst)
write.csv(Allsum_he, file = file.path("Wy_Ed_Jobs", "allsum_he.csv"))

henow<- facultydata%>%
  filter(Archive_Date == max(Archive_Date))

henowsum <- henow %>%
  group_by(Category) %>%
  summarize(
    Sum = n()
  ) %>%
  ungroup()%>%
  mutate(Institution = "Total")

henowinstsum<- henow %>%
  group_by(Category, Institution)%>%
  summarize(
    Sum = n()
  ) %>%
  ungroup()%>%
  select(Category, Sum, Institution)

Allnow_he<- rbind(henowsum, henowinstsum)

write.csv(Allnow_he, file = file.path("Wy_Ed_Jobs", "allnow_he.csv"))
```



