---
title: "R Job Scrape"
author: "Mark Perkins"
date: "2025-09-18"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("k12_he_classification.R")
```
# This Markdown file contains all the code to scrape data from Wyoming's k12 and higher education job postings

## Part 1: Wyoming K12 Data

### Loop K12 data pulled from all districts that use applitrack
```{r loop with district sites on applitrack, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(readr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Read the CSV file
csv_file <- "Frontline_job_links.csv"
job_links <- read_csv(csv_file)

# fetch_applitrack_postings() replaces the old RSelenium loop entirely --
# Output.asp (the endpoint default.aspx's own inline script injects via
# document.write()) is fetched directly instead of rendering default.aspx
# in a browser and waiting for that injection to happen. Each district is
# logged individually via safe_scrape() so one district's outage (a few
# genuinely return HTTP 500 from Applitrack's own servers, independent of
# this scraper -- confirmed 2026-08-02) doesn't block the rest of the CSV.
all_jobs_data <- list()

for (i in 1:nrow(job_links)) {
  url <- job_links$JobSite[i]
  school_district <- job_links$`School District`[i]

  # tenant_path is everything between applitrack.com/ and /onlineapp/ in
  # the district's own URL.
  tenant_path <- sub(".*applitrack\\.com/([^/]+)/onlineapp.*", "\\1", url, ignore.case = TRUE)

  district_jobs <- safe_scrape(
    school_district,
    scrape_fn = function() fetch_applitrack_postings(tenant_path),
    expected_cols = c("title", "position", "position2", "date_posted", "location", "closing_date")
  )

  if (nrow(district_jobs) == 0) {
    district_jobs <- data.frame(
      title = "No jobs", position = NA, position2 = NA, date_posted = NA,
      location = NA, closing_date = NA, stringsAsFactors = FALSE
    )
  }
  district_jobs$school_district <- school_district

  all_jobs_data[[length(all_jobs_data) + 1]] <- district_jobs
}

all_jobs_df <- bind_rows(all_jobs_data)

# Join with original job_links for extra metadata (this supplies the `url`
# column combinedclean expects -- one job-board URL per district, not a
# per-posting deep link, matching the original scraper's behavior).
all_jobs_df <- left_join(all_jobs_df, job_links, by = c("school_district" = "School District"))

# Save data frame to CSV file
write.csv(all_jobs_df, "all_job_listings.csv", row.names = FALSE)

```

### Loop k12 data from districts that use Tedd k12
```{r tedk12, message=FALSE, warning=FALSE, echo=TRUE}

# Load required libraries
library(rvest)
library(dplyr)
library(readr)
library(purrr)
source("scrape_helpers.R")

# Read the CSV file containing the URLs
tedjoblinks <- read.csv("tedk12_job_links.csv", stringsAsFactors = FALSE)

# Initialize an empty data frame to store the job data
all_ted_data <- data.frame(
  title = character(),
  date_posted = character(),
  position = character(),
  location = character(),
  url = character(),
  stringsAsFactors = FALSE
)

# Loop through each URL in the CSV file. No Selenium session here (plain
# read_html against a static page), so each URL just needs its own
# tryCatch + log entry -- one dead/changed URL no longer aborts every URL
# after it in the CSV.
for (i in 1:nrow(tedjoblinks)) {
  url <- tedjoblinks$Job.Link[i]  # Using the Job.Link column for URLs

  jobs <- tryCatch({
    # Read the HTML content of the page
    page <- read_html(url)

    # Extract job title, posting date, type, and location
    result <- page %>%
      html_nodes("tr") %>% # Assuming each job is within a <tr> element
      map_df(~{
        title <- .x %>%
          html_node("td:nth-child(1) a") %>%
          html_text(trim = TRUE)

        date_posted <- .x %>%
          html_node("td:nth-child(2)") %>%
          html_text(trim = TRUE)

        position <- .x %>%
          html_node("td:nth-child(3)") %>%
          html_text(trim = TRUE)

        location <- .x %>%
          html_node("td:nth-child(4)") %>%
          html_text(trim = TRUE)

        data.frame(
          title = title,
          date_posted = date_posted,
          position = position,
          location = location,
          url = url,  # Add the URL to the data frame
          stringsAsFactors = FALSE
        )
      })

    log_scrape_result(url, status = if (nrow(result) > 0) "ok" else "empty", n_rows = nrow(result))
    result
  }, error = function(e) {
    message("tedk12: error scraping ", url, ": ", conditionMessage(e))
    log_scrape_result(url, status = "error", n_rows = 0, error_message = conditionMessage(e))
    data.frame(title = character(), date_posted = character(), position = character(),
               location = character(), url = character(), stringsAsFactors = FALSE)
  })

  # Append the jobs data to the all_jobs_data data frame
  all_ted_data <- bind_rows(all_ted_data, jobs)
}

# Remove rows with NA or "Job Title" in the job_title column
all_ted_data <- all_ted_data %>%
  filter(!is.na(title) & title != "Job Title")

all_ted_data<-left_join(all_ted_data, tedjoblinks, by = c("url" = "Job.Link"))


# Save the extracted data to a CSV file
write.csv(all_ted_data, "all_tedk12_job_listings.csv", row.names = FALSE)

```

### Loop k12 data from all districts that use springer school
```{r jobs from spring school, message=FALSE, warning=FALSE, echo=TRUE}

library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# springer_job_links.csv's districts turned out to be split across two
# platforms despite the shared filename/history: most are SchoolSpring
# (api.schoolspring.com -- unprotected despite the interactive UI domain
# being behind Incapsula), but Johnson County SD1 migrated to RedRoverK12
# (an unauthenticated GraphQL API, found by tracing real network traffic
# with chromote). Both replace the old RSelenium infinite-scroll-and-click
# scraper entirely.
#
# RedRoverK12 requires a numeric org ID per district that isn't derivable
# from its URL slug alone; known IDs are listed here as they're found the
# same way (chromote network trace of the real site). A district that
# migrates to this platform in the future and isn't yet in this table will
# safely fall through to being treated as SchoolSpring and logged as an
# error rather than silently returning nothing.
redrover_org_ids <- c(jcsd1 = "3146", hotsprings1 = "3034")

springerjoblinks <- read.csv("springer_job_links.csv", stringsAsFactors = FALSE)

all_springer_data <- list()

for (i in 1:nrow(springerjoblinks)) {
  url <- springerjoblinks$`Job.Link`[i]
  district <- springerjoblinks$District[i]

  is_redrover <- grepl("redroverk12\\.com", url, ignore.case = TRUE)

  district_jobs <- if (is_redrover) {
    org_slug <- sub(".*/org/([^/?]+).*", "\\1", url, ignore.case = TRUE)
    org_id <- redrover_org_ids[[org_slug]]
    safe_scrape(
      district,
      scrape_fn = function() fetch_redrover_postings(org_id, org_slug),
      expected_cols = c("Title", "Location", "Posted_Date", "Link")
    )
  } else {
    domain_name <- sub("^https?://", "", url)
    domain_name <- sub("/$", "", domain_name)
    safe_scrape(
      district,
      scrape_fn = function() fetch_schoolspring_postings(domain_name),
      expected_cols = c("Title", "Location", "Posted_Date", "Link")
    )
  }

  if (nrow(district_jobs) > 0) {
    district_jobs$District <- district
    district_jobs$url_source <- url
    all_springer_data[[length(all_springer_data) + 1]] <- district_jobs
  }
}

all_springer_data <- if (length(all_springer_data) > 0) {
  bind_rows(all_springer_data)
} else {
  data.frame(Title = character(0), Location = character(0), Posted_Date = character(0),
             Link = character(0), District = character(0), url_source = character(0))
}

# Match the schema the rest of the K-12 pipeline expects (title/date_posted/
# position/location/url/District). `url` is the district's own job-board
# URL (matching the Applitrack/Frontline loader's convention of one URL per
# district, not a per-posting deep link), not the per-job Link this scrape
# also captured; `position` is intentionally NA -- combinedclean's
# classify_k12_position() recomputes it from `title` for every source, so
# the scraped value is discarded downstream regardless.
all_springer_data <- all_springer_data %>%
  transmute(
    title = Title,
    date_posted = Posted_Date,
    position = NA_character_,
    location = Location,
    url = url_source,
    District = District
  )

write.csv(all_springer_data, "all_springer_job_listings.csv", row.names = FALSE)

```

### Combine all the k12 data include a few manual pulls from unique district sites
#### Be sure to update your manually scraped data
#### This will populate your app folder for your Shiny application
```{r combine all the data into one dataframe, echo=TRUE, warning=FALSE, message=FALSE}
library(stringr)
library(tidyverse)
library(dplyr)
library(lubridate)


standardize_date <- function(x) {

  # Convert factor to character safely
  x <- as.character(x)

  # Remove timezone text like "(UTC)"
  x <- str_remove(x, "\\s*\\(.*\\)$")

  # Parse known formats
  parsed <- parse_date_time(
    x,
    orders = c(
      "b d Y h:M p",   # Oct 23 2025 6:00 AM
      "B d Y h:M p",   # October 23 2025 6:00 AM
      "ymd",
      "mdy",
      "dmy",
      "Y-m-d H:M:S"
    ),
    tz = "UTC",
    quiet = TRUE
  )

  as.Date(parsed)
}



frontline<- read.csv("all_job_listings.csv")%>%
  rename(url = JobSite)

frontline<-  dplyr::select(frontline, title, date_posted, position, location, url, school_district)%>%
  rename(District = school_district)

ted<- read.csv("all_tedk12_job_listings.csv")

springer<- read.csv("all_springer_job_listings.csv")

# The 12 districts not on any major platform were previously hand-
# maintained in otherjobs.xlsx (no code in this repo ever wrote that
# file -- it was 5 months stale). Replaced with a real pipeline: WSBA's
# statewide vacancies page (clean structured data, but confirmed
# incomplete -- misses ~60-75% of real postings, systematically dropping
# classified/support/substitute/coaching roles) combined with each
# district's own page (heuristic per-platform extraction, deduplicated
# against that district's WSBA entries by normalized title). See
# misc_district_scrapers.R's header comment for the full platform
# breakdown and known limitations.
source("scrape_helpers.R")
source("direct_api_scrapers.R")
source("misc_district_scrapers.R")

other <- safe_scrape(
  "Miscellaneous K-12 districts (WSBA + own pages)",
  scrape_fn = function() {
    fetch_all_misc_district_postings(
      chromote_session_factory = function() chromote::ChromoteSession$new()
    )
  },
  expected_cols = c("title", "date_posted", "position", "location", "url", "District")
)

# Laramie Montessori Charter School: not a school district at all (so it
# has no natural home in misc_district_registry, which is keyed by
# District), but was found to have its own clean structured source
# (Paylocity) while investigating Wyoming's charter schools -- see
# direct_api_scrapers.R::fetch_paylocity_jobs(). Snowy Range Academy, the
# other real charter school found, already surfaces via WSBA with no
# extra code needed since WSBA already treats it as a standalone org.
laramie_montessori <- safe_scrape(
  "Laramie Montessori Charter School",
  scrape_fn = function() fetch_paylocity_jobs("70f7d03b-6c9f-4106-8e70-9d781a8bbcba", "Laramie-Montessori-School-Inc"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)
if (nrow(laramie_montessori) > 0) {
  laramie_montessori <- data.frame(
    title = laramie_montessori$Title,
    date_posted = laramie_montessori$Posted_Date,
    position = NA_character_,
    location = laramie_montessori$Location,
    url = laramie_montessori$Link,
    District = "Laramie Montessori Charter School",
    stringsAsFactors = FALSE
  )
  other <- dplyr::bind_rows(other, laramie_montessori)
}

frontline <- frontline %>%
  mutate(date_posted = standardize_date(date_posted))

ted <- ted %>%
  mutate(date_posted = standardize_date(date_posted))

springer <- springer %>%
  mutate(date_posted = standardize_date(date_posted))

other <- other %>%
  mutate(date_posted = standardize_date(date_posted))


combined<- rbind(frontline, ted, springer, other)%>%
  mutate(Archive_Date = Sys.Date())



file_name <- paste0("combined_", Sys.Date(), ".csv")

# Write the data to a CSV file with the new file name
write.csv(combined, file=file.path('Archivek12_Data',file_name))

# Categorize positions in the "position" column of the "combinedclean" dataset.
# classify_k12_position() lives in k12_he_classification.R (sourced above) so
# this week's raw jobs-table classification and the full-archive rebuild
# below can't silently drift apart.

combinedclean <- combined %>%
  mutate(position = classify_k12_position(title)) %>%
  dplyr::select(title, date_posted, position, location, url, District)

write.csv(combinedclean, file=file.path('Wy_Ed_Jobs','combinedclean.csv'))


#Munge the archived data and send files to Shiny
csv_files <- list.files("Archivek12_Data", pattern = "\\.csv$", full.names = TRUE)

combined_k12_data <- csv_files %>%
  lapply(function(file) read.csv(file, colClasses = c("Archive_Date" = "character"))) %>%
  bind_rows() %>%
  select(-X, -date_posted)

combined_k12_data <- combined_k12_data %>%
  mutate(Archive_Date = case_when(
    grepl("/", Archive_Date) ~ as.Date(Archive_Date, format = "%m/%d/%Y"),
    grepl("-", Archive_Date) ~ as.Date(Archive_Date, format = "%Y-%m-%d"),
    TRUE ~ as.Date(NA)  # Corrected this line
  ))

dates <- as.data.frame(unique(combined_k12_data$Archive_Date))


combined_k12_data$Archive_Date <- as.Date(combined_k12_data$Archive_Date)

###################################################
# Create Categories
# position/Category/Broad_Category classification and District name
# canonicalization all live in k12_he_classification.R (sourced in setup)
# so this full-archive rebuild can't drift from the current-week block above.

combinedclean <- combined_k12_data %>%
  mutate(position = classify_k12_position(title)) %>%
  dplyr::select(title, Archive_Date, position, location, url, District)

combinedclean <- combinedclean %>%
  mutate(District = canonicalize_k12_district(District))

k12jobs <- combinedclean %>%
  filter(position == "Teacher")

k12jobs <- k12jobs %>%
  mutate(Category = classify_k12_subject(title))

k12jobs <- k12jobs %>%
  mutate(Broad_Category = classify_k12_broad_category(Category))

write.csv(k12jobs, file=file.path('Wy_Ed_Jobs','k12jobanalysis.csv'))


#Database for all dates by category
# Dedup key is title+location, not title alone: two different schools in the
# same district legitimately post the same generic title (e.g. "Elementary
# Teacher") for two different, real openings; n_distinct(title) alone would
# silently collapse those into a single counted posting.
#
# The Total row is computed as the SUM of the per-district counts below, not
# as its own independent n_distinct() over every district's rows combined.
# Some scrapers fall back to a generic location placeholder (literally the
# string "District") when they can't extract a real school name, and two
# different districts can both produce that same generic title+location
# combination for two genuinely different real postings; deduping across
# district boundaries would silently collapse those into one and undercount
# the Total relative to its own parts.
k12sumdistrict <- k12jobs %>%
  group_by(Broad_Category, Archive_Date, District) %>%
  summarize(
    sum = n_distinct(paste(title, location))
  ) %>%
  ungroup()

k12sum <- k12sumdistrict %>%
  group_by(Broad_Category, Archive_Date) %>%
  summarize(sum = sum(sum)) %>%
  ungroup() %>%
  mutate(District = "Total") %>%
  select(Broad_Category, Archive_Date, District, sum)

Allsum <- bind_rows(k12sum, k12sumdistrict)
write.csv(Allsum, file=file.path('Wy_Ed_Jobs','allsum.csv'))

#Database for all data now by category
k12now <- k12jobs %>%
  filter(Archive_Date == max(Archive_Date))

k12districtnowsum <- k12now %>%
  group_by(Broad_Category, District) %>%
  summarize(
    Sum = n_distinct(paste(title, location))
  ) %>%
  ungroup() %>%
  select(Broad_Category, Sum, District)

k12nowsum <- k12districtnowsum %>%
  group_by(Broad_Category) %>%
  summarize(Sum = sum(Sum)) %>%
  ungroup() %>%
  mutate(District = "Total")

Allnow <- bind_rows(k12nowsum, k12districtnowsum)

write.csv(Allnow, file=file.path('Wy_Ed_Jobs','allnow.csv'))

list<-unique(k12jobs$District)
write.csv(list, "list.csv")
```


## Time to scrape Wyoming Higher Education Data
### This chunk scrapes LCCC's data
```{r Get Jobs from LCCC, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# LCCC is on the same NEOGOV platform as Casper/Central/Gillette/Western,
# just under the governmentjobs.com domain instead of schooljobs.com --
# fetch_neogov_postings() takes the domain as a parameter for exactly this
# reason. Replaces the old RSelenium scraper (manual scroll + wait-for-
# element polling) with a single direct HTTP call.
lccc_raw <- safe_scrape(
  "Laramie County Community College",
  scrape_fn = function() fetch_neogov_postings("https://www.governmentjobs.com", "lcccwy"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

lccc <- lccc_raw %>%
  mutate(Institution = "Laramie County Community College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(lccc)

```

### This pulls data from Casper College
```{r casper college, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

casper_raw <- safe_scrape(
  "Casper College",
  scrape_fn = function() fetch_neogov_postings("https://www.schooljobs.com", "caspercollege"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

casper <- casper_raw %>%
  mutate(Institution = "Casper College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(casper)

```


### This pulls jobs data from Western Wyoming
```{r western wyoming, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Western is on the same PeopleAdmin platform as Eastern/Sheridan/
# Northwest, not NEOGOV -- a prior investigation mistyped the domain as
# "wwccwy.peopleadmin.com" (double-c), got NXDOMAIN, and wrongly concluded
# Western had migrated to schooljobs.com/careers/westernwyoming (a real
# NEOGOV agency slug that happens to return a valid "0 jobs found" page,
# not Western's actual career site). The real domain is
# "wwcwy.peopleadmin.com" (single-c) -- confirmed live with 46 real open
# postings, silently missed by the NEOGOV version for an unknown period.
western_raw <- safe_scrape(
  "Western Wyoming Community College",
  scrape_fn = function() fetch_peopleadmin_atom("https://wwcwy.peopleadmin.com/postings/all_jobs", "Western Wyoming Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

western <- western_raw %>%
  mutate(Institution = "Western Wyoming Community College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(western)

```


### This pulls data from Central Wyoming college
```{r central wyoming, message=FALSE, echo=TRUE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

central_raw <- safe_scrape(
  "Central Wyoming College",
  scrape_fn = function() fetch_neogov_postings("https://www.schooljobs.com", "cwc"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

central <- central_raw %>%
  mutate(Institution = "Central Wyoming College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(central)

```

### This pulls jobs data from Eastern Wyoming college
```{r Eastern, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Eastern's own published Atom feed replaces the old RSelenium scraper
# entirely -- see direct_api_scrapers.R::fetch_peopleadmin_atom(). No
# browser, no pagination, no CSS selectors to drift.
eastern_raw <- safe_scrape(
  "Eastern Wyoming Community College",
  scrape_fn = function() fetch_peopleadmin_atom("https://ewc.peopleadmin.com/postings/all_jobs", "Eastern Wyoming Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

eastern <- eastern_raw %>%
  mutate(Institution = "Eastern Wyoming Community College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(eastern)

```

### This pulls data Gillette college
```{r gillette, message=FALSE, echo=TRUE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

gillette_raw <- safe_scrape(
  "Gillette College",
  scrape_fn = function() fetch_neogov_postings("https://www.schooljobs.com", "gillettecollege"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

gillette <- gillette_raw %>%
  mutate(Institution = "Gillette College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(gillette)

```
### This pulls data from Sheridan College
```{r sheridan, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Sheridan is on the same PeopleAdmin platform as Eastern Wyoming --
# confirmed by matching asset hashes/scripts -- so the same Atom feed
# approach applies. Replaces the old RSelenium scraper (which navigated to
# every individual job's detail page just to read its posting date).
sheridan_raw <- safe_scrape(
  "Sheridan College",
  scrape_fn = function() fetch_peopleadmin_atom("https://jobs.sheridan.edu/postings/all_jobs", "Sheridan College Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

sheridan <- sheridan_raw %>%
  mutate(Institution = "Sheridan College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(sheridan)

```

### This pulls data from Northwest College
```{r Northwest, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# Northwest is also on the same PeopleAdmin platform, white-labeled under
# the simplehire.com domain -- confirmed by matching asset hashes/scripts
# despite the different-looking hostname and previously different
# selectors. Same Atom feed approach as Eastern/Sheridan.
northwest_raw <- safe_scrape(
  "Northwest College",
  scrape_fn = function() fetch_peopleadmin_atom("https://northwestcollege.simplehire.com/postings/all_jobs", "Northwest College Campus"),
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

northwest <- northwest_raw %>%
  mutate(Institution = "Northwest College") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(northwest)

```



### This pulls data from the University of Wyoming
```{r university of Wyoming}
library(dplyr)
source("scrape_helpers.R")
source("direct_api_scrapers.R")

# UW's Oracle Cloud HCM recruiting platform exposes a public JSON REST API
# (see direct_api_scrapers.R::fetch_uw_postings()) that fully replaces the
# old RSelenium scraper -- no infinite-scroll simulation, no
# findElements()-based text scraping, no waiting on JS to render.
UW_raw <- safe_scrape(
  "University of Wyoming",
  scrape_fn = fetch_uw_postings,
  expected_cols = c("Title", "Location", "Posted_Date", "Link")
)

UW <- UW_raw %>%
  mutate(Institution = "University of Wyoming") %>%
  select(Title, Location, Posted_Date, Institution, Link)

print(UW)

```

### Combine all the Higher Education data
#### This will populate your app folder for your Shiny application
```{r munge he data, message=FALSE, warning=FALSE, echo=TRUE}
library(dplyr)
library(writexl)
library(tidyverse)
library(readxl)

# Combine all datasets
hedata <- rbind(lccc, casper, western, central, eastern, gillette, sheridan, northwest, UW)

hedata$Posted_Date<- as.character(hedata$Posted_Date)

hedata <- hedata %>%
  mutate(Archive_Date = Sys.Date())

# Save data with a time stamp
file_name <- paste0("hedata_", Sys.Date(), ".xlsx")

write_xlsx(hedata, path = file_name)

write_xlsx(hedata, path = file.path("Archived_HE_Data", file_name))
write_xlsx(hedata, path = file.path("Wy_Ed_Jobs", "hedata.xlsx"))

csv_files <- list.files("Archived_HE_Data", pattern = "\\.xlsx$", full.names = TRUE)

combined_HE_data <- csv_files %>%
  lapply(read_xlsx) %>%   
  bind_rows()

combined_HE_data$Archive_Date <- as.Date(combined_HE_data$Archive_Date)

# Fix historical institution-name typos before anything downstream keys off
# Institution, so a college's history doesn't silently split across two
# spellings (see canonicalize_he_institution() in k12_he_classification.R).
combined_HE_data <- combined_HE_data %>%
  mutate(Institution = canonicalize_he_institution(Institution))

# Job_Type/Category classification lives in k12_he_classification.R (sourced
# in setup). Adjunct/pooled titles get their own Job_Type, separate from
# "Instructor/Teacher/Faculty", so a standing adjunct-pool posting isn't
# counted the same as full-time faculty hiring.
combined_cat <- combined_HE_data %>%
  mutate(Job_Type = classify_he_job_type(Title))

facultydata <- combined_cat %>%
  filter(Job_Type == "Instructor/Teacher/Faculty") %>%
  mutate(Category = classify_he_faculty_category(Title))
write.csv(facultydata, "facultydata.csv")
hesum <- facultydata %>%
  group_by(Category, Archive_Date) %>%
  summarize(
    sum = n()
  ) %>%
  ungroup()%>%
  mutate(Institution = "Total")%>%
  select(Category, Archive_Date, Institution, sum)

hesuminst<- facultydata%>%
  group_by(Category, Archive_Date, Institution)%>%
  summarise(
    sum = n()
  )%>%
  ungroup()

Allsum_he<-rbind(hesum, hesuminst)
write.csv(Allsum_he, file = file.path("Wy_Ed_Jobs", "allsum_he.csv"))

henow<- facultydata%>%
  filter(Archive_Date == max(Archive_Date))

henowsum <- henow %>%
  group_by(Category) %>%
  summarize(
    Sum = n()
  ) %>%
  ungroup()%>%
  mutate(Institution = "Total")

henowinstsum<- henow %>%
  group_by(Category, Institution)%>%
  summarize(
    Sum = n()
  ) %>%
  ungroup()%>%
  select(Category, Sum, Institution)

Allnow_he<- rbind(henowsum, henowinstsum)

write.csv(Allnow_he, file = file.path("Wy_Ed_Jobs", "allnow_he.csv"))
```



